### 2016-06-23 paper.tex
Report

\documentclass[12pt,a4paper,onecolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{K. R. Prajwal \\ Sagar Sahani \and  Ketaki Vaidya  \\Anya Chaturvedi }
\title{Summer Report On The Capacitated K-Center Problem}
\begin{document}
\maketitle
\section{Introduction to our Problem}
The capacitated K-center problem is a basic facility location problem, where one is asked to locate K facilities in a graph and to assign vertices to these facilities. In doing this we minimize
the maximum distance from a vertex to the facility to which it is assigned. Moreover, each facility
may be assigned at most L vertices including itself. This problem is known to be NP-hard.\\
We show our attempts at solving this problem, counter examples as learnt by us and few basic implementations of the same. The implementations include finding the optimal using the integer program and a partially accurate local search algorithm.
\section{A Look At The K-center problem}
Given n vertices with specified distances, one wants to build k facilities at different vertices and minimize the maximum distance of a vertex to a facility. This problem is NP-hard. An approximation algorithm with a factor of $\rho$ ,for a minimization problem,is
a polynomial time algorithm that guarantees a solution with cost at most $\rho$ times
the cost of an optimal solution. Approximation algorithms for the basic K-center
problem have been very well studied and are known to be optimal.
These schemes present natural methods for obtaining an approximation factor of 2.Given a complete undirected graph G = (V, E) with distances $d(v_i, v_j) \in N$ satisfying the triangle inequality, find a subset $S \subseteq V$ with $|S| = k$.\\ \textbf{Input:}\\1. The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2. An
upper bound on the number of centers K.\\
\textbf{Formal Definition:}\\
$$\min_{S \subseteq V}\max_{v \in V}\min_{s \in S}d(v,s)$$
where d is the distance function.\\
This is much similar to the problem of placing k disks such that all points are covered in the set V and thus finding the minimum radius for the disks.
%\begin{center}

%\begin{figure}[h]
 % \includegraphics[scale=0.5]{kcenter.png}
  %\caption{HELLO}
  %\label{fig:intro}
%\end{figure}
%\end{center}
\section{The Capacitated K-Center}
The capacitated K-center problem is nothing but a generalization of the K-center problem. We have to
output a set of at most K centers,as well as an assignment of vertices to centers. No more than L vertices may be assigned to a single center. Under these constraints,we
wish to minimize the maximum distance between a vertex u and its assigned center
$\varphi$(u). \\
\textbf{Input:}\\1. The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2. An
upper bound on the number of centers K.\\3. A maximum load L.\\\textbf{Formal Definition:}\\
$$ \min_{S \subseteq V}\max_{u \in V}d(u,\varphi(u)) $$such that,   $$|\{u|\varphi(u) = v\}|\leq L \forall v \in S,$$\\where,   $$\varphi : V \rightarrow S.$$
The first polynomial time approximation
algorithm for this problem was with an approximation factor of 10. Later a 6-approximation was found which is the best up till date while a 5-approximation works when we can assign multiple centers at a single vertex without including the vertex in L.

\section{Checking the Feasibility of the Input Graph}
Flow
\section{The Integer Program}
\section{Local Search Algorithm}
\section{Existing Algorithm (6-approximation)}
\section{Observations made}
\subsection{Failed Attempts}
\subsection{Counter Examples}
\subsection{Current Scenario}
\end{document}

### 2016-06-27 graphgen.py
Added Star dataset generator

@@ -1,0 +1,70 @@
+import snap
+import random
+import networkx as nx
+from collections import namedtuple
+
+__author__ = 'K R Prajwal'
+
+class Graph(object):
+	def __init__(self, specs):
+		self.k = specs.k
+		self.l = specs.l
+
+		if specs.struct == 'stars':
+			self.N = self.k*self.l
+			self.p = specs.p	# supplementary edge probability
+			self.starGraph()
+
+		elif specs.struct == 'random':
+			self.N = specs.N 
+			self.edges = specs.M
+			self.randomGraph()
+
+		else:
+			raise ValueError('Invalid specifications!')
+
+		self.nxGraph = self.NXify()
+
+	def initAdj(self):
+		self.adj = dict()
+		for x in range(self.N):
+			for y in range(self.N):
+				self.adj[(x,y)] = 0
+		for i in xrange(self.N):
+			self.adj[(i,i)] = 1
+
+	def randomGraph(self):
+		UGraph = snap.GenRndGnm(snap.PUNGraph, self.N, self.edges)
+		self.initAdj()
+
+		for EI in UGraph.Edges():
+			self.adj[(EI.GetSrcNId(),EI.GetDstNId())] = 1
+			self.adj[(EI.GetDstNId(), EI.GetSrcNId())] = 1
+
+	def starGraph(self):
+		self.initAdj()
+		non_centers = set([x for x in xrange(self.N)])
+		star_centers = random.sample(list(non_centers), self.k)
+		for x in star_centers: non_centers.remove(x)
+		non_centers = list(non_centers)
+		random.shuffle(non_centers)
+		star_clients = [non_centers[i:i + self.l - 1] for i in xrange(0, len(non_centers), self.l - 1)]
+
+		for center, clients in zip(star_centers, star_clients):
+			for client in clients:
+				self.adj[(center,client)] = self.adj[(client, center)] = 1
+
+		for x in range(self.N):
+			for y in range(self.N):
+				self.adj[(x,y)] = int(random.random() < self.p)
+
+
+	#Storing the random graph in G
+	def NXify(self):
+		G = nx.Graph()
+		G.add_nodes_from([x for x in xrange(self.N)])
+		for i in xrange(self.N):
+			for j in xrange(i,self.N):
+				if self.adj[(i,j)]:
+					G.add_edge(i,j)
+		return G

### 2016-06-27 ls.py

@@ -1,35 +1,8 @@
 import networkx as nx
 import snap
 from random import shuffle
-from collections import defaultdict
-
-#Generating a random graph using snap
-def randomGraph(n,edges):
-	UGraph = snap.GenRndGnm(snap.PUNGraph, n, edges)
-	adj = dict()
-	for x in range(n):
-		for y in range(n):
-			adj[(x,y)] = 0
-	for EI in UGraph.Edges():
-		adj[(EI.GetSrcNId(),EI.GetDstNId())] = 1
-		adj[(EI.GetDstNId(), EI.GetSrcNId())] = 1
-	for i in xrange(n):
-		adj[(i,i)] = 1
-	for x in range(n):
-		for y in range(n):
-			print adj[(x,y)],
-		print
-	return adj
-
-#Storing the random graph in G
-def getGraph(N,adj):
-	G = nx.Graph()
-	G.add_nodes_from([x for x in xrange(N)])
-	for i in xrange(N):
-		for j in xrange(i,N):
-			if adj[(i,j)]:
-				G.add_edge(i,j)
-	return G
+from collections import defaultdict, namedtuple
+from graphgen import Graph
 
 #Obtaining a random set S of initial k centers
 def getS(G,k):
@@ -94,10 +67,12 @@ def doOneSwaps(G, S, L):
 		Vmax = getVmax(G, S, L)
 	return S
 
-N, M = 10,30
-adj = randomGraph(N,M)
-k, L = 5,3
-G = getGraph(N,adj)
+k, L, p = 5, 3, 0.3
+N = k*L
+starSpec = namedtuple('specs', 'struct k l p')
+specs = starSpec('stars', k, L, p)
+graph = Graph(specs)
+G = graph.nxGraph
 S = getS(G,k)
 S = doOneSwaps(G, S, L)
 H = defaultdict(list)

### 2016-06-27 graphgen.py
Fixed all bugs for star dataset

@@ -55,8 +55,10 @@ class Graph(object):
 				self.adj[(center,client)] = self.adj[(client, center)] = 1
 
 		for x in range(self.N):
-			for y in range(self.N):
-				self.adj[(x,y)] = int(random.random() < self.p)
+			for y in range(x + 1,self.N):
+				if self.adj[(x,y)] != 1:
+					self.adj[(x,y)] = int(random.random() < self.p)
+					self.adj[(y,x)] = int(random.random() < self.p)
 
 
 	#Storing the random graph in G

### 2016-06-27 ls.py

@@ -3,6 +3,8 @@ import snap
 from random import shuffle
 from collections import defaultdict, namedtuple
 from graphgen import Graph
+import matplotlib.pyplot as plt 
+import pprint
 
 #Obtaining a random set S of initial k centers
 def getS(G,k):
@@ -61,13 +63,13 @@ def getVmax(G, S, L):
 
 #changing S and Vmax by one swaps so as to achieve the max flow possible after each obtained S
 def doOneSwaps(G, S, L):
-	Vmax = getVmax(G, S, L)
+	Vmax = getVmax(G, S[:], L)
 	while nx.maximum_flow_value(getFlowGraph(G, Vmax, L), 's', 't') > nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't'):
 		S = Vmax
-		Vmax = getVmax(G, S, L)
+		Vmax = getVmax(G, S[:], L)
 	return S
 
-k, L, p = 5, 3, 0.3
+k, L, p = 5, 3, 0.4
 N = k*L
 starSpec = namedtuple('specs', 'struct k l p')
 specs = starSpec('stars', k, L, p)
@@ -98,5 +100,19 @@ if nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't') == N:
 					H[s].append(v)
 else:
 	print "Failed!"
+edges = 0
+#print graph.adj
+adj = [[0 for _ in xrange(N)] for _ in xrange(N)]
+for key, val in graph.adj.iteritems():
+	if val == 1:
+		adj[key[0]][key[1]] = 1
+		edges += 1
+
+edges -= N
+edges /= 2
+
+print "Edges: ", edges
 print S
 print H
+
+#pprint.pprint(adj)

### 2016-06-29 OPTIMAL1.py
Add files via upload

@@ -1,0 +1,75 @@
+import snap
+from pulp import *
+
+def randomGraph(n,edges):
+	UGraph = snap.GenRndGnm(snap.PUNGraph, n, edges)
+	#Graph = snap.LoadEdgeList(snap.PUNGraph, "facebook_combined.txt", 0, 1, ' ')
+	#snap.PrintInfo(Graph, "Facebook Data Set")
+	#UGraph = snap.GetRndSubGraph(Graph,n)
+	adj = dict()
+	for x in range(n):
+		for y in range(n):
+			adj[(x,y)] = 0
+	for EI in UGraph.Edges():
+		adj[(EI.GetSrcNId(),EI.GetDstNId())] = 1
+		adj[(EI.GetDstNId(), EI.GetSrcNId())] = 1
+	for i in xrange(n):
+		adj[(i,i)] = 1
+	#for x in range(n):
+	#	for y in range(n):
+	#		print adj[(x,y)],
+	#	print
+	return adj
+
+N=input("No. of vertices (n<4039):")
+edges=input("No. of edges:")
+adj = randomGraph(N,edges)
+edges = sum([sum(x) for x in adj])/2
+L = N/10
+
+# declare your variables
+cen = dict(zip([i for i in range(N)],[0 for i in range(N)]))		
+cen = LpVariable.dicts("cen",cen, 0, 1,LpInteger)
+
+assignments = {}
+for i in range(N):
+	for j in range(N):
+		assignments[(i,j)] = adj[(i,j)]
+
+assignments = LpVariable.dicts("assignments",assignments,0,1)
+
+# defines the problem
+prob = LpProblem("problem", LpMinimize)
+
+# defines the objective function to minimize : sum(y)
+prob += lpSum([cen[i] for i in range(N)])
+
+############# Constraint definitions ###################
+
+# sum(x_ij) <= L*y[i]
+for i in xrange(N):
+	prob += lpSum([assignments[(i,j)] for j in xrange(N)]) <= L*cen[i]
+
+# sum(x_ij) = 1 for all j
+for j in xrange(N):
+	prob += lpSum([assignments[(i,j)] for i in xrange(N)]) == 1
+
+# y_i >= x_ij for all i,j
+for i in xrange(N):
+	for j in xrange(N):
+		prob += assignments[(i,j)] <= cen[i]
+#the assignment can be done only when the edge is present
+for i in xrange(N):
+	for j in xrange(N):
[…]

### 2016-06-29 OPTIMAL1.py
Update OPTIMAL1.py

@@ -3,9 +3,6 @@ from pulp import *
 
 def randomGraph(n,edges):
 	UGraph = snap.GenRndGnm(snap.PUNGraph, n, edges)
-	#Graph = snap.LoadEdgeList(snap.PUNGraph, "facebook_combined.txt", 0, 1, ' ')
-	#snap.PrintInfo(Graph, "Facebook Data Set")
-	#UGraph = snap.GetRndSubGraph(Graph,n)
 	adj = dict()
 	for x in range(n):
 		for y in range(n):
@@ -15,10 +12,6 @@ def randomGraph(n,edges):
 		adj[(EI.GetDstNId(), EI.GetSrcNId())] = 1
 	for i in xrange(n):
 		adj[(i,i)] = 1
-	#for x in range(n):
-	#	for y in range(n):
-	#		print adj[(x,y)],
-	#	print
 	return adj
 
 N=input("No. of vertices (n<4039):")

### 2016-06-30 ls.py
Update ls.py

@@ -1,10 +1,35 @@
 import networkx as nx
 import snap
 from random import shuffle
-from collections import defaultdict, namedtuple
-from graphgen import Graph
-import matplotlib.pyplot as plt 
-import pprint
+from collections import defaultdict
+
+#Generating a random graph using snap
+def randomGraph(n,edges):
+	UGraph = snap.GenRndGnm(snap.PUNGraph, n, edges)
+	adj = dict()
+	for x in range(n):
+		for y in range(n):
+			adj[(x,y)] = 0
+	for EI in UGraph.Edges():
+		adj[(EI.GetSrcNId(),EI.GetDstNId())] = 1
+		adj[(EI.GetDstNId(), EI.GetSrcNId())] = 1
+	for i in xrange(n):
+		adj[(i,i)] = 1
+	for x in range(n):
+		for y in range(n):
+			print adj[(x,y)],
+		print
+	return adj
+
+#Storing the random graph in G
+def getGraph(N,adj):
+	G = nx.Graph()
+	G.add_nodes_from([x for x in xrange(N)])
+	for i in xrange(N):
+		for j in xrange(i,N):
+			if adj[(i,j)]:
+				G.add_edge(i,j)
+	return G
 
 #Obtaining a random set S of initial k centers
 def getS(G,k):
@@ -18,10 +43,9 @@ def getFlowGraph(G, S, L):
 	N = len(G.nodes())
 	#for common nodes in V and S make separate keys for S
 	for x in G.nodes():
+		FG.add_node(x)
 		if x in S:
 			FG.add_node(x + N)
-		else:
-			FG.add_node(x)
 
 	FG.add_nodes_from(['s','t'])
 	edges = set(G.edges())
@@ -63,18 +87,16 @@ def getVmax(G, S, L):
 
 #changing S and Vmax by one swaps so as to achieve the max flow possible after each obtained S
 def doOneSwaps(G, S, L):
-	Vmax = getVmax(G, S[:], L)
+	Vmax = getVmax(G, S, L)
 	while nx.maximum_flow_value(getFlowGraph(G, Vmax, L), 's', 't') > nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't'):
 		S = Vmax
-		Vmax = getVmax(G, S[:], L)
+		Vmax = getVmax(G, S, L)
 	return S
 
-k, L, p = 5, 3, 0.4
-N = k*L
[…]

### 2016-06-30 ls.py
Fixed a minor bug in Flow network creation

@@ -20,8 +20,7 @@ def getFlowGraph(G, S, L):
 	for x in G.nodes():
 		if x in S:
 			FG.add_node(x + N)
-		else:
-			FG.add_node(x)
+		FG.add_node(x)
 
 	FG.add_nodes_from(['s','t'])
 	edges = set(G.edges())
@@ -69,10 +68,11 @@ def doOneSwaps(G, S, L):
 		Vmax = getVmax(G, S[:], L)
 	return S
 
-k, L, p = 5, 3, 0.4
+k, L = 10, 5
 N = k*L
-starSpec = namedtuple('specs', 'struct k l p')
-specs = starSpec('stars', k, L, p)
+edges = 130
+starSpec = namedtuple('specs', 'struct N M k l')
+specs = starSpec('random', N, edges, k, L)
 graph = Graph(specs)
 G = graph.nxGraph
 S = getS(G,k)
@@ -114,5 +114,3 @@ edges /= 2
 print "Edges: ", edges
 print S
 print H
-
-#pprint.pprint(adj)

### 2016-06-30 graphgen.py
Update graphgen.py

@@ -3,8 +3,6 @@ import random
 import networkx as nx
 from collections import namedtuple
 
-__author__ = 'K R Prajwal'
-
 class Graph(object):
 	def __init__(self, specs):
 		self.k = specs.k

### 2016-06-30 paper.tex
Update paper.tex

@@
 \usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
-\author{K. R. Prajwal \\ Sagar Sahani \and  Ketaki Vaidya  \\Anya Chaturvedi }
+\usepackage{float}
+\usepackage{newunicodechar}
+\newunicodechar{ﬁ}{fi}
+\newunicodechar{ﬂ}{fl}
+\author{Anya Chaturvedi \\ Ketaki Vaidya \and K. R. Prajwal \\ Sagar Sahni  }
 \title{Summer Report On The Capacitated K-Center Problem}
@@
 \section{Introduction to our Problem}
-The capacitated K-center problem is a basic facility location problem, where one is asked to locate K facilities in a graph and to assign vertices to these facilities. In doing this we minimize
-the maximum distance from a vertex to the facility to which it is assigned. Moreover, each facility
-may be assigned at most L vertices including itself. This problem is known to be NP-hard.\\
+The capacitated K-center problem is basically a facility location problem, where one is asked to locate K facilities in a graph and to assign vertices to these facilities. In doing this we minimize
+the maximum distance from a vertex to the facility to which it is assigned while keeping in mind that each facility may be assigned at most L vertices including itself.
+This problem is known to be NP-hard.\\
 We show our attempts at solving this problem, counter examples as learnt by us and few basic implementations of the same.
@@
 \section{A Look At The K-center problem}
+The problem taken up by us is actually a generalization of the K-center problem which we will explain here.
 Given n vertices with specified distances, one wants to build k facilities at different vertices and minimize the maximum distance of a vertex to a facility.
 This problem is NP-hard.
-An approximation algorithm with a factor of $\rho$ ,for a minimization problem,is
-a polynomial time algorithm that guarantees a solution with cost at most $\rho$ times
-the cost of an optimal solution. Approximation algorithms for the basic K-center
-problem have been very well studied and are known to be optimal.
-These schemes present natural methods for obtaining an approximation factor of 2.Given a complete undirected graph G = (V, E) with distances $d(v_i, v_j) \in N$ satisfying the triangle inequality, find a subset $S \subseteq V$ with $|S| = k$.\\ \textbf{Input:}\\1.
+An approximation algorithm with a factor of $\eta$ ,for a minimization problem,is
+a polynomial time algorithm that guarantees a solution with cost at most $\eta$ times the cost of an optimal solution.
+For the basic K-center methods have been presented for obtaining an approximation factor of 2.
+Given a complete undirected graph G = (V, E) with distances $d(v_i, v_j) \in N$ satisfying the triangle inequality, find a subset $S \subseteq V$ with $|S| = k$.\\ \textbf{Input:}\\1.
 The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2.
@@
 \section{Checking the Feasibility of the Input Graph}
-Flow
+We say that, if we solve the capacitated K-center problem then it will be equivalent to getting the minimum value of W for which G(W) has a capacitated dominating set of size k, where G(W) refers to the graph having all edges with edge weight less than or equal to W.\\
+We can easily set up such an equivalence if we slightly modify our problem.
+Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$, $S \subseteq V$ is a capacitated dominating set if there exists a mapping $f : V \backslash S \rightarrow S$ (domination mapping) such that:\\\\ 1.
+$\forall v \in V \backslash S,\forall s \in S,f(v) = s \Longrightarrow (v,s) \in E$\\ \\2.
+$\forall s \in S,| \{ v \in V \backslash S | f(v) = s \} | \leq c(s)$\\ \\In the new version of the k-center problem, the goal is to get a set S of k vertices and an assignment $h : V \backslash S \rightarrow S$ of every vertex (in $V \backslash S$) to an open center such that the longest distance between a vertex and a center it is assigned to is minimum and no facility is assigned more vertices than its capacity.
+Note that, the assignment is not for all vertices in V .
+We are making the assumption that every center serves itself and the capacity (L(v)) of a vertex $v \in V$ is the maximum number of clients it can serve (excluding itself).
+\\\\Now we can say that, solving the capacitated k-center problem is equivalent to getting the minimum value of W for which G(W) has a capacitated dominating set of size k.
+$S \subseteq V$ is an optimal solution to the capacitated K-center problem if and only if w(S) is the minimum value of W for which the graph G(W) has a capacitated dominating set of size k.
+It is also easy to verify that a capacitated dominating set of size k in $G(w(S))^i$, for some i and some optimal solution S, forms an i-approximation for the k-center problem.\\ But the capacitated dominating set problem is an NP-complete problem.
+So, we cannot get a capacitated dominating set of size k in polynomial time, unless $P = NP$ Similar to the uncapacitated version the capacitated version too is hard to approximate within a factor of 2.
+\subsection{Verification using a Network Flow }
+Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$, checking whether $S \in V$ is a capacitated dominating set can be viewed as a network problem.
+Construct a directed graph $G_S = (V_S,E_S)$ as follows:\\\\ 1.
+$V_S = V \cup \{s,t\}$\\\\ 2.
+$E_S = \{(s,v_i) | v_i \in V \backslash S \} \cup \{(s_i,t) | s_i \in S \}\cup \{(v_i,s_i) | v_i \in V \backslash S \wedge s_i \in S \wedge (v_i,s_i) \in E \}$\\\\ Let $c_S : E_S \rightarrow N$ be the capacity function such that, $$c_S(e_{uv}) =\left\{ \begin{array}{cc}(c(u),  &  v = t \\\\ 1, & otherwise \end{array}\right.$$
+In the final graph $G_S$ we add two more vertices s (source) and t (sink) to the vertex set of G.
+We add directed edges from s to all vertices in $V \backslash S$, from each vertex in $V \backslash S$ to its neighbours in S and each vertex in S to t.
+We take the capacity function to be equal to the capacity of the source vertex for edges incident on t and to be equal to 1 for every other edge in $E_S$.
+\\
+\begin{center}
+ \begin{figure}[H]
+ \begin{center}
+ \includegraphics[scale=1]{flow.png}
+ \end{center}
+  \caption{The flow network}
+  \label{Figure 1}
+\end{figure}
+ \end{center} Now it is easy to verify that, S is a capacitated dominating set in G if and only if $G_S$ has a maximum coverage of $|V \backslash S|$ from s to t equal to the total vertices in the graph.
+
 \section{The Integer Program}
+Linear programming is a mathematical technique for maximizing or minimizing a linear function of several variables such as output or cost.
+The decision variables with respect to which the optimum is obtained can come out to be fractional or any real number.
+An integer programming problem is a mathematical optimization or feasibility program in which
+some or all of the variables are restricted to be integers which is the major difference it has from linear programming. Ours is a problem where we
+wish to minimize the maximum distance between a vertex u and its assigned center thus our integer program is framed as:
+\\\\
+\textbf{Variables:}\begin{enumerate}
+\item \textit{\textbf{cen}} - an integer dictionary which specifies the centers among the vertices
+where if $cen[i]=1$ then the $i^{th}$ index vertex is taken to be a center otherwise not.\item \textit{\textbf{assignments}} - dictionary $assignments[i][j]=1$ will represent that the $j^th$ index vertex is assigned to the center created at the $i^th$ index vertex, we initialize it with the adjacency matrix
+\item \textit{\textbf{N}} - represents the total number of vertices
+\item \textit{\textbf{adj}} - a dictionary which stores the adjacency matrix of the graph
+
+\end{enumerate}
+
+\begin{center}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{1.png}
+  \caption{Code}
+  \label{Figure 2}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{2.png}
+  \caption{Code}
+  \label{Figure 3}
+\end{figure}
+\end{center}
+\textbf{Objective Function:}\\
+\hspace{15mm} $$z=\sum_{i=1}^{N}cen[i]$$
+
+\textbf{Constraints:}
+\begin{enumerate}
+\item $\forall i \sum_{j=1}^{N}assignments[i][j]\leq L*cen[i]$\\\hspace{1cm}\ldots makes sure no more than L vertices are assigned to a center
+\item $\forall j \sum_{i=1}^{N}assignments[i][j] = 1$\\\hspace{1cm}\ldots a vertex can be assigned only to a single center
+\item $\forall i \, \forall j \, assignments[i][j] \leq cen[i]$\\\hspace{1cm}\ldots a vertex can only be assigned to a second vertex if the second vertex is a center
+\item $\forall i , \forall j \, assignments[i][j] \leq adj[i][j]$\\\hspace{1cm}\ldots 
+assignment of vertices can only be done if the edge is present in the original graph
+
+\end{enumerate}
+
 \section{Local Search Algorithm}
-\section{Existing Algorithm (6-approximation)}
+Local search can be used on problems that can be formulated as finding a solution maximizing a criterion among a number of candidate solutions.
+A local search algorithm starts from a candidate solution and then iteratively moves to a neighbour solution.
+We move from solution to solution in the space of candidate solutions (the search space) by applying local changes, until a solution optimal is found.
+We have used a local search algorithm which was formed by Aounon.
+It doesnt work on a set of graphs but we get the solution for some general graphs we tested on.Here, we start with a set S of random k vertices in graph G .
+Let S be the set of all k vertex sets which are formed by replacing one vertex in S by a vertex in V (one-swap vertex sets).
+We look for the set in S which maximizes the number of dominated vertices.
+If the optimum set dominates more vertices than S then we set S to that set and continue the process till we have reached a local optima.
+We do the assignments through a network flow graph.\\\\
+\textbf{Algorithm:}\\
+$S \leftarrow {v1, v2,…., vk}$\\
+$S' \leftarrow {one-swap\: vertex\: sets\: of\: S_g}$\\
+$V_{max} \leftarrow arg\: max_{ V \in S} \: MaxFlow(G_{V} , c_{V} )$\\
+$while \: MaxFlow(G_{V_{max}}; c_{V_{max}}) > MaxFlow(G_S; c_S)\: do$ $ \par S \leftarrow V_{max} \par S' \leftarrow {one-swap\: vertex \:sets \:of \:S}\par V_{max} \leftarrow argmax _{V \in S}\: MaxFlow(G_V , c_V )$\\
+$end\: while$\\
+$if\: MaxFlow(G_S , c_S) = n - k\: then \par
+for \: all \: v \in V \:do \par \hspace{1cm} h(v) = s:\: if\: fmax(v, s) = 1\par
+end \: for\par
+return\: S,\: h$\\
+$end\: if$\\
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{a.png}
+  \caption{Code}
+  \label{Figure 4}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{b.png}
+  \caption{Code}
+  \label{Figure 5}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{c.png}
+  \caption{Code}
+  \label{Figure 6}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{d.png}
+  \caption{Code}
+  \label{Figure 7}
+\end{figure}
+
+\section{Star Graph Generation}
+In an attempt to try our programs on a more clustered data set, this program was implemented such that in this star graphs are formed which are sparsely connected to each other by edges which are added to the graph based on a probability p.
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{g1.png}
+  \caption{Code}
+  \label{Figure 8}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{g2.png}
+  \caption{Code}
+  \label{Figure 9}
+\end{figure}
+
 \section{Observations made}
-\subsection{Failed Attempts}
+This section basically focuses on all our trials and errors we had during our intern on this topic along with few of the concepts learnt which provide the base for these trials.
+\subsection{Lower Bound on K}
+
+\subsection{Our Attempts}
+\begin{itemize}
+\item In our attempt we start by applying the 2-approximation K-center algorithm on the given graph.
+We then tried to apply what we had learnt by reading the OPT + 1 local search algorithm of the min-degree spanning tree from section 2.6 of Williamson \& Schmoy.
+Effectively,if possible we transferred the load from the highest capacity nodes to lower ones through a contiguous sequence of edge assignment swaps until we reach a vertex with lower capacity as visible in the figure.
+\\
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.25]{d3.jpg}
+  \caption{reassignment through propagation}
+  \label{Figure 8}
+\end{center}
+\end{figure}
+\textbf{Algorithm:}
+\begin{enumerate}
+\item Start with k' centers of $G^2$ with no regard to capacity L using the 2-approximation algorithm for uncapacitated k-center.
+\item $C \leftarrow$ set of all k-centers
+\item $C^l \leftarrow$ subset of C such that $\forall C \in C^l, C$ covers exactly l clients.
+\item In each phase:\\
+\hspace{1cm}$l \leftarrow$ the maximum degree of any center\\
+\hspace{1cm}$C_l \leftarrow$ set of all centers with degree l
+\item Subphase (while there are center with degree l do:)
+\begin{enumerate}
+\item Choose a client v assigned to some center in $C_l$.
+\item Choose another client $C_m$ (m<l) of minimum degree among all the centers v is connected to or some $C_m$ which is connected through some alternate manner of center then non center and finally with v.
+\end{enumerate}
+\end{enumerate}
+This is done in order to reduce the maximum number of assignments to a particular center so as to reach the capacity L.
+This propagation is possible only when a non center is connected to two or more centers and hence reassignment can be done.\\ But we still might have too few centers in dense cliques while just sufficient in other parts or maybe even having residual capacities in sparse areas.
+We also have a counter example for the same.
+\\
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.25]{d1.jpg}
+  \caption{Counter Example}
+  \label{Figure 9}
+\end{center}
+\end{figure} Maybe moving to higher powers of G may contribute to requiring less centers at regions where at present the centers are suffice.\\Hence, from $G^2$ we move to $G^4$.
+Here, each center with its clients forming a star graph will transform into a clique.\begin{figure}
+\begin{center}
+\includegraphics[scale=0.25]{d2.jpg}
+  \caption{Clique formation}
+  \label{Figure 10}
+\end{center}
+\end{figure} With such a change we might me able to merge few cliques by placing a center on a common node of two cliques(while removing their respective centers) such that both the cliques add up to give vertices less than L.
+\\
+Following this we have free centers available which we can place in dense cliques with high degree of vertices.
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.3]{d4.jpg}
+  \caption{Merging}
+  \label{Figure 11}
+\end{center}
+\end{figure}
+Like here we obtain one extra center. The problem still remains on how to keep obtaining such centers other than by merging and then placing them at an appropriate position.\\
+Further, we try to come up with some kind of data structure that might help us make some claims on the lower bound on K.
+
+\end{itemize}
 \subsection{Counter Examples}

### 2016-07-01 paper.tex
Update paper.tex

@@
 Later a 6-approximation was found which is the best up till date while a 5-approximation works when we can assign multiple centers at a single vertex without including the vertex in L.
-
+This was our problem for the summer.
+\\Initially we went through the 2.6 and 9.3 sections of Williamson Schmoy which solve the min degree spanning tree problem which is also NP-hard and got to know of methods like local search used to create approximation algorithms.\\Certifying a graph for an algorithm not only has to ensure that we can show whether a solution is possible for G or not it also involves showing that if a solution is not possible in G then it is not even possible in $G^2,G^3]ldots$
 \section{Checking the Feasibility of the Input Graph}
@@
 $end\: while$\\
-$if\: MaxFlow(G_S , c_S) = n - k\: then \par
-for \: all \: v \in V \:do \par \hspace{1cm} h(v) = s:\: if\: fmax(v, s) = 1\par
-end \: for\par
-return\: S,\: h$\\
+$if\: MaxFlow(G_S , c_S) = n - k\: then \par for \: all \: v \in V \:do \par \hspace{1cm} h(v) = s:\: if\: fmax(v, s) = 1\par end \: for\par return\: S,\: h$\\
 $end\: if$\\
@@
 \subsection{Lower Bound on K}
-
+Lets say we make some partition on our input graph such that each partition has two types of vertices.
+Inner and boundary, the inner vertices are the ones within the particular partition while the boundary vertices are inner vertices which even have edges to other partitions.
+Let the $i^th$ partition be represented by its inner vertice $C_i$ and its boundary vertices as a function of $C_i$ as $B(C_i)$.\\
+Since we know K vertices can cover up to L vertices so the max vertices than can be covered is $V = K*L$.
+Hence K can be taken to be approximately $\lceil V/L\rceil$.
+Thus if we try forming a lower bound so as to claim that the graph requires atleast these many vertices as equal to the bound then it might be of help.
+\\Here, in the partitioning as described above, for the vertices other than the boundary vertices we can say that they can only be covered by vertices of their own partition thus we need to open centers in the partition itself for such vertices.
+Thus, if we say there are p partitions then $\sum_{i=1}^{p}\lceil (C_i-B(C_i))/L\rceil$ vertices are required atleast to cover the graph and hence this comes to be a lower bound.
+\\ This has been presented in a research paper already but the fact that we are not really involving the boundary vertices did not sink in and though it did not work out but we toyed for some time with ideas of somehow involving the boundary vertices.
+We thought with the current vertices the remaining capacity i.e.
+$\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$ we may be able to cover some or even all of the boundary vertices.
+Through this we can decide opening more centers or shifting the centers so as to cover more boundary vertice.
+But it always depends upon the connectivity of the particular graph and what kind of partition we take and that was where we left this.
 \subsection{Our Attempts}
@@
 \\
-\begin{figure}
+\begin{figure}[H]
 \begin{center}
@@
   \caption{reassignment through propagation}
-  \label{Figure 8}
+  \label{Figure 13}
 \end{center}
@@
 This propagation is possible only when a non center is connected to two or more centers and hence reassignment can be done.\\ But we still might have too few centers in dense cliques while just sufficient in other parts or maybe even having residual capacities in sparse areas.
-We also have a counter example for the same.
-\\
-\begin{figure}
+We also have a counter example for the same as shown in the figure below.
+The centers are represented by the rectangular marks on the vertices.
+The left most center is covering many clients within a distance of <=2 where as the same cannot be said for the other centers.\\
+\begin{figure}[H]
 \begin{center}
@@
   \caption{Counter Example}
-  \label{Figure 9}
+  \label{Figure 12}
 \end{center}
 \end{figure} Maybe moving to higher powers of G may contribute to requiring less centers at regions where at present the centers are suffice.\\Hence, from $G^2$ we move to $G^4$.
-Here, each center with its clients forming a star graph will transform into a clique.\begin{figure}
+Here, each center with its clients forming a star graph will transform into a clique.The same shown in the figure below.\begin{figure}[H]
 \begin{center}
@@
 \end{center}
-\end{figure} With such a change we might me able to merge few cliques by placing a center on a common node of two cliques(while removing their respective centers) such that both the cliques add up to give vertices less than L.
+\end{figure} With such a change we might be able to merge few cliques by placing a center on a common node of two cliques(while removing their respective centers) such that both the cliques add up to give vertices less than L.
 \\
 Following this we have free centers available which we can place in dense cliques with high degree of vertices.
-\begin{figure}
+Like in the figure below in the nodes that were centers in $G^2$ are represented by square labels in the left figure and diamond label on the right while the one which we replace them by in $G^4$ is represent by the square in the right figure.
+\begin{figure}[H]
 \begin{center}
@@
 Like here we obtain one extra center. The problem still remains on how to keep obtaining such centers other than by merging and then placing them at an appropriate position.\\
-Further, we try to come up with some kind of data structure that might help us make some claims on the lower bound on K.
+Further, we try to come up with some kind of data structure that might help us make some claims on the lower bound on K. \begin{figure}
+
+\end{figure}
+As above we make a level structure with the cliques in set $C_l$ as taken before at level l.After a reassignment is performed, the structure changes, because, always the cliques are taken to be a center and its neighbors.
+After a reassignment, the set of neighbors of (more than or equal to 2) centers change, and also, their capacities change, thus moving them to different levels than present.
+\\\textbf{Theorem:}
+When there can be no more edge reassignments, then no center at level l, has an edge of length <= 4 to any node in level l’ >= l+2 for all l. 
+\\
+\textbf{Proof:}
+After there can be no more reassignments, let there exists such a center C at a level l which has an edge to some node P belonging to some level l’ >= l + 2.
+Let C’ be the center covering the node P.
+Then we can do a reassignment step such that P gets assigned to C instead of C` thereby moving C` one level down and C one level up.
+Thus the max degree can decrease this way removing one clique at a time.
+
+\begin{figure}
+
+\end{figure}
+
+This contradicts our assumption that no more reassignment is possible.
 

### 2016-07-04 paper.tex
Update paper.tex

@@
 \usepackage{graphicx}
-\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
+\usepackage[margin=1in]{geometry}
+\usepackage{mathpazo}
 \usepackage{float}
+
+\usepackage{algorithmic}
 \usepackage{newunicodechar}
@@
 \newunicodechar{ﬂ}{fl}
+
 \author{Anya Chaturvedi \\ Ketaki Vaidya \and K. R. Prajwal \\ Sagar Sahni  }
@@
 the maximum distance from a vertex to the facility to which it is assigned while keeping in mind that each facility may be assigned at most L vertices including itself.
-This problem is known to be NP-hard.\\
+This problem is known to be NP-hard.
+
 We show our attempts at solving this problem, counter examples as learnt by us and few basic implementations of the same.
@@
 For the basic K-center methods have been presented for obtaining an approximation factor of 2.
-Given a complete undirected graph G = (V, E) with distances $d(v_i, v_j) \in N$ satisfying the triangle inequality, find a subset $S \subseteq V$ with $|S| = k$.\\ \textbf{Input:}\\1.
-The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2.
-An
-upper bound on the number of centers K.\\
+Given a complete undirected graph G = (V, E) with distances $d(v_i, v_j) \in N$ satisfying the triangle inequality, find a subset $S \subseteq V$ with $|S| = k$.\\\\
+ \textbf{Input:}\\1. The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2. An
+upper bound on the number of centers K.\\\\
 \textbf{Formal Definition:}\\
 $$\min_{S \subseteq V}\max_{v \in V}\min_{s \in S}d(v,s)$$
-where d is the distance function.\\
+where d is the distance function.
+
 This is much similar to the problem of placing k disks such that all points are covered in the set V and thus finding the minimum radius for the disks.
@@
 wish to minimize the maximum distance between a vertex u and its assigned center
-$\varphi$(u). \\
+$\varphi$(u). \\\\
 \textbf{Input:}\\1. The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2. An
-upper bound on the number of centers K.\\3. A maximum load L.\\\textbf{Formal Definition:}\\
-$$ \min_{S \subseteq V}\max_{u \in V}d(u,\varphi(u)) $$such that,   $$|\{u|\varphi(u) = v\}|\leq L \forall v \in S,$$\\where,   $$\varphi : V \rightarrow S.$$
+upper bound on the number of centers K.\\3. A maximum load L.\\\\
+\textbf{Formal Definition:}\\
+$$ \min_{S \subseteq V}\max_{u \in V}d(u,\varphi(u)) $$such that,   $$|\{u|\varphi(u) = v\}|\leq L \forall v \in S,$$\\where,   $$\varphi : V \rightarrow S.$$\\
 The first polynomial time approximation
@@
 This was our problem for the summer.
-\\Initially we went through the 2.6 and 9.3 sections of Williamson Schmoy which solve the min degree spanning tree problem which is also NP-hard and got to know of methods like local search used to create approximation algorithms.\\Certifying a graph for an algorithm not only has to ensure that we can show whether a solution is possible for G or not it also involves showing that if a solution is not possible in G then it is not even possible in $G^2,G^3]ldots$
+
+Initially we went through the 2.6 and 9.3 sections of Williamson Schmoy which solve the min degree spanning tree problem which is also NP-hard and got to know of methods like local search used to create approximation algorithms.
+
+Certifying a graph for an algorithm not only has to ensure that we can show whether a solution is possible for G or not it also involves showing that if a solution is not possible in G then it is not even possible in $G^2,G^3\ldots$
 \section{Checking the Feasibility of the Input Graph}
-We say that, if we solve the capacitated K-center problem then it will be equivalent to getting the minimum value of W for which G(W) has a capacitated dominating set of size k, where G(W) refers to the graph having all edges with edge weight less than or equal to W.\\
+We say that, if we solve the capacitated K-center problem then it will be equivalent to getting the minimum value of W for which G(W) has a capacitated dominating set of size k, where G(W) refers to the graph having all edges with edge weight less than or equal to W.
+
 We can easily set up such an equivalence if we slightly modify our problem.
-Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$, $S \subseteq V$ is a capacitated dominating set if there exists a mapping $f : V \backslash S \rightarrow S$ (domination mapping) such that:\\\\ 1.
-$\forall v \in V \backslash S,\forall s \in S,f(v) = s \Longrightarrow (v,s) \in E$\\ \\2.
-$\forall s \in S,| \{ v \in V \backslash S | f(v) = s \} | \leq c(s)$\\ \\In the new version of the k-center problem, the goal is to get a set S of k vertices and an assignment $h : V \backslash S \rightarrow S$ of every vertex (in $V \backslash S$) to an open center such that the longest distance between a vertex and a center it is assigned to is minimum and no facility is assigned more vertices than its capacity.
+Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$, $S \subseteq V$ is a capacitated dominating set if there exists a mapping $f : V \backslash S \rightarrow S$ (domination mapping) such that:\begin{enumerate}
+
+\item $\forall v \in V \backslash S,\forall s \in S,f(v) = s \Longrightarrow (v,s) \in E$\\ \item $\forall s \in S,| \{ v \in V \backslash S | f(v) = s \} | \leq c(s)$
+\end{enumerate}In the new version of the k-center problem, the goal is to get a set S of k vertices and an assignment $h : V \backslash S \rightarrow S$ of every vertex (in $V \backslash S$) to an open center such that the longest distance between a vertex and a center it is assigned to is minimum and no facility is assigned more vertices than its capacity.
 Note that, the assignment is not for all vertices in V .
 We are making the assumption that every center serves itself and the capacity (L(v)) of a vertex $v \in V$ is the maximum number of clients it can serve (excluding itself).
-\\\\Now we can say that, solving the capacitated k-center problem is equivalent to getting the minimum value of W for which G(W) has a capacitated dominating set of size k.
+
+Now we can say that, solving the capacitated k-center problem is equivalent to getting the minimum value of W for which G(W) has a capacitated dominating set of size k. 
 $S \subseteq V$ is an optimal solution to the capacitated K-center problem if and only if w(S) is the minimum value of W for which the graph G(W) has a capacitated dominating set of size k.
-It is also easy to verify that a capacitated dominating set of size k in $G(w(S))^i$, for some i and some optimal solution S, forms an i-approximation for the k-center problem.\\ But the capacitated dominating set problem is an NP-complete problem.
+It is also easy to verify that a capacitated dominating set of size k in $G(w(S))^i$, for some i and some optimal solution S, forms an i-approximation for the k-center problem.
+
+But the capacitated dominating set problem is an NP-complete problem.
 So, we cannot get a capacitated dominating set of size k in polynomial time, unless $P = NP$ Similar to the uncapacitated version the capacitated version too is hard to approximate within a factor of 2.
@@
 Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$, checking whether $S \in V$ is a capacitated dominating set can be viewed as a network problem.
-Construct a directed graph $G_S = (V_S,E_S)$ as follows:\\\\ 1.
-$V_S = V \cup \{s,t\}$\\\\ 2.
-$E_S = \{(s,v_i) | v_i \in V \backslash S \} \cup \{(s_i,t) | s_i \in S \}\cup \{(v_i,s_i) | v_i \in V \backslash S \wedge s_i \in S \wedge (v_i,s_i) \in E \}$\\\\ Let $c_S : E_S \rightarrow N$ be the capacity function such that, $$c_S(e_{uv}) =\left\{ \begin{array}{cc}(c(u),  &  v = t \\\\ 1, & otherwise \end{array}\right.$$
+Construct a directed graph $G_S = (V_S,E_S)$ as follows:\begin{enumerate}
+\item $V_S = V \cup \{s,t\}$
+\item $E_S = \{(s,v_i) | v_i \in V \backslash S \} \cup \{(s_i,t) | s_i \in S \}\cup \{(v_i,s_i) | v_i \in V \backslash S \wedge s_i \in S \wedge (v_i,s_i) \in E \}$\end{enumerate} Let $c_S : E_S \rightarrow N$ be the capacity function such that, $$c_S(e_{uv}) =\left\{ \begin{array}{cc}(c(u),  &  v = t \\\\ 1, & otherwise \end{array}\right.$$
 In the final graph $G_S$ we add two more vertices s (source) and t (sink) to the vertex set of G.
@@
 wish to minimize the maximum distance between a vertex u and its assigned center thus our integer program is framed as:
-\\\\
-\textbf{Variables:}\begin{enumerate}
-\item \textit{\textbf{cen}} - an integer dictionary which specifies the centers among the vertices
-where if $cen[i]=1$ then the $i^{th}$ index vertex is taken to be a center otherwise not.\item \textit{\textbf{assignments}} - dictionary $assignments[i][j]=1$ will represent that the $j^th$ index vertex is assigned to the center created at the $i^th$ index vertex, we initialize it with the adjacency matrix
-\item \textit{\textbf{N}} - represents the total number of vertices
-\item \textit{\textbf{adj}} - a dictionary which stores the adjacency matrix of the graph
-
-\end{enumerate}
+\\
 
@@
 \hspace{15mm} $$z=\sum_{i=1}^{N}cen[i]$$
-
+\\
+\textbf{Variables:}\begin{enumerate}
+\item \textit{\textbf{cen}} - an integer dictionary which specifies the centers among the vertices
+where if $cen[i]=1$ then the $i^{th}$ index vertex is taken to be a center otherwise not.\item \textit{\textbf{assignments}} - dictionary $assignments[i][j]=1$ will represent that the $j^th$ index vertex is assigned to the center created at the $i^th$ index vertex, we initialize it with the adjacency matrix
+\item \textit{\textbf{N}} - represents the total number of vertices
+\item \textit{\textbf{adj}} - a dictionary which stores the adjacency matrix of the graph 
+\end{enumerate}
 \textbf{Constraints:}
@@
 We move from solution to solution in the space of candidate solutions (the search space) by applying local changes, until a solution optimal is found.
-We have used a local search algorithm which was formed by Aounon.
-It doesnt work on a set of graphs but we get the solution for some general graphs we tested on.Here, we start with a set S of random k vertices in graph G .
+We have used a local search algorithm which was formed by Aounon. It doesnt work on a set of graphs but we get the solution for some general graphs we tested on.
+
+Here, we start with a set S of random k vertices in graph G .
 Let S be the set of all k vertex sets which are formed by replacing one vertex in S by a vertex in V (one-swap vertex sets).
@@
 We do the assignments through a network flow graph.\\\\
-\textbf{Algorithm:}\\
-$S \leftarrow {v1, v2,…., vk}$\\
-$S' \leftarrow {one-swap\: vertex\: sets\: of\: S_g}$\\
-$V_{max} \leftarrow arg\: max_{ V \in S} \: MaxFlow(G_{V} , c_{V} )$\\
-$while \: MaxFlow(G_{V_{max}}; c_{V_{max}}) > MaxFlow(G_S; c_S)\: do$ $ \par S \leftarrow V_{max} \par S' \leftarrow {one-swap\: vertex \:sets \:of \:S}\par V_{max} \leftarrow argmax _{V \in S}\: MaxFlow(G_V , c_V )$\\
-$end\: while$\\
-$if\: MaxFlow(G_S , c_S) = n - k\: then \par for \: all \: v \in V \:do \par \hspace{1cm} h(v) = s:\: if\: fmax(v, s) = 1\par end \: for\par return\: S,\: h$\\
-$end\: if$\\
+\textbf{Algorithm:}
+\begin{algorithmic}[1]
+\STATE $S \leftarrow {v1, v2,…., vk}$
+\STATE $S' \leftarrow {one-swap\: vertex\: sets\: of\: S}$
+\WHILE {$MaxFlow(G_{V_{max}}, c_{V_{max}}) > MaxFlow(G_S,c_S)$}
+\STATE $S \leftarrow V_{max}$
+\STATE $S' \leftarrow {one-swap vertex sets of S}$
+\STATE $V_{max} \leftarrow argmax _{V \in S} MaxFlow(G_V , c_V )$
+\ENDWHILE 
+\IF{$MaxFlow(G_S , c_S) = n - k$}
+\FORALL {$v \in V$}
+\IF{$f_{max}(v,s)=1$}
+\STATE $h(v) = s$
+\ENDIF
+\ENDFOR
+\RETURN $S, h$
+\ENDIF
+\end{algorithmic}
 
@@
 Inner and boundary, the inner vertices are the ones within the particular partition while the boundary vertices are inner vertices which even have edges to other partitions.
-Let the $i^th$ partition be represented by its inner vertice $C_i$ and its boundary vertices as a function of $C_i$ as $B(C_i)$.\\
+Let the $i^th$ partition be represented by its inner vertice $C_i$ and its boundary vertices as a function of $C_i$ as $B(C_i)$.
+
 Since we know K vertices can cover up to L vertices so the max vertices than can be covered is $V = K*L$.
@@
 Thus if we try forming a lower bound so as to claim that the graph requires atleast these many vertices as equal to the bound then it might be of help.
-\\Here, in the partitioning as described above, for the vertices other than the boundary vertices we can say that they can only be covered by vertices of their own partition thus we need to open centers in the partition itself for such vertices.
+
+Here, in the partitioning as described above, for the vertices other than the boundary vertices we can say that they can only be covered by vertices of their own partition thus we need to open centers in the partition itself for such vertices.
 Thus, if we say there are p partitions then $\sum_{i=1}^{p}\lceil (C_i-B(C_i))/L\rceil$ vertices are required atleast to cover the graph and hence this comes to be a lower bound.
-\\ This has been presented in a research paper already but the fact that we are not really involving the boundary vertices did not sink in and though it did not work out but we toyed for some time with ideas of somehow involving the boundary vertices.
+
+ This has been presented in a research paper already but the fact that we are not really involving the boundary vertices did not sink in and though it did not work out but we toyed for some time with ideas of somehow involving the boundary vertices.
 We thought with the current vertices the remaining capacity i.e.
@@
 \textbf{Algorithm:}
-\begin{enumerate}
-\item Start with k' centers of $G^2$ with no regard to capacity L using the 2-approximation algorithm for uncapacitated k-center.
-\item $C \leftarrow$ set of all k-centers
-\item $C^l \leftarrow$ subset of C such that $\forall C \in C^l, C$ covers exactly l clients.
-\item In each phase:\\
-\hspace{1cm}$l \leftarrow$ the maximum degree of any center\\
-\hspace{1cm}$C_l \leftarrow$ set of all centers with degree l
-\item Subphase (while there are center with degree l do:)
-\begin{enumerate}
-\item Choose a client v assigned to some center in $C_l$.
-\item Choose another client $C_m$ (m<l) of minimum degree among all the centers v is connected to or some $C_m$ which is connected through some alternate manner of center then non center and finally with v.
-\end{enumerate}
-\end{enumerate}
+\begin{algorithmic}[1]
+\STATE Start with k' centers of $G^2$ with no regard to capacity L using the 2-approximation algorithm for uncapacitated k-center.
+\STATE $C \leftarrow$ set of all k-centers
+\STATE $C^l \leftarrow$ subset of C such that$\forall C \in C^l$, C covers exactly l clients.
+\STATE In each phase:\\
+\STATE \hspace{1cm}$l \leftarrow$ the maximum degree of any center\\
+\STATE \hspace{1cm}$C_l \leftarrow$ set of all centers with degree l
+\STATE Subphase
+\WHILE {there are center with degree l} 
+\STATE Choose a client v assigned to some center in $C_l$.
+\STATE Choose another client $C_m$ (m<l) of minimum degree among all the centers v is connected to or some $C_m$ which is connected through some alternate manner of center then non center and finally with v.
+\ENDWHILE
+\end{algorithmic}
 This is done in order to reduce the maximum number of assignments to a particular center so as to reach the capacity L.
-This propagation is possible only when a non center is connected to two or more centers and hence reassignment can be done.\\ But we still might have too few centers in dense cliques while just sufficient in other parts or maybe even having residual capacities in sparse areas.
+This propagation is possible only when a non center is connected to two or more centers and hence reassignment can be done.
+
+But we still might have too few centers in dense cliques while just sufficient in other parts or maybe even having residual capacities in sparse areas.
 We also have a counter example for the same as shown in the figure below.
@@
 \end{center}
-\end{figure} Maybe moving to higher powers of G may contribute to requiring less centers at regions where at present the centers are suffice.\\Hence, from $G^2$ we move to $G^4$.
-Here, each center with its clients forming a star graph will transform into a clique.The same shown in the figure below.\begin{figure}[H]
+\end{figure} Maybe moving to higher powers of G may contribute to requiring less centers at regions where at present the centers are suffice.
+
+Hence, from $G^2$ we move to $G^4$. Here, each center with its clients forming a star graph will transform into a clique.The same shown in the figure below.\begin{figure}[H]
 \begin{center}
@@
 \end{figure} With such a change we might be able to merge few cliques by placing a center on a common node of two cliques(while removing their respective centers) such that both the cliques add up to give vertices less than L.
-\\
+
 Following this we have free centers available which we can place in dense cliques with high degree of vertices.
@@
 \end{figure}
-Like here we obtain one extra center. The problem still remains on how to keep obtaining such centers other than by merging and then placing them at an appropriate position.\\
+Like here we obtain one extra center. The problem still remains on how to keep obtaining such centers other than by merging and then placing them at an appropriate position.
+
 Further, we try to come up with some kind of data structure that might help us make some claims on the lower bound on K. \begin{figure}
@@
 After a reassignment, the set of neighbors of (more than or equal to 2) centers change, and also, their capacities change, thus moving them to different levels than present.
-\\\textbf{Theorem:}
+\\\\\textbf{Theorem:}
 When there can be no more edge reassignments, then no center at level l, has an edge of length <= 4 to any node in level l’ >= l+2 for all l. 
-\\
+\\\\
 \textbf{Proof:}

### 2016-07-04 OPTIMAL1.py
Added Unit Square graph creation script

@@ -1,7 +1,9 @@
 import snap
 from pulp import *
+from unitSquare import UnitSquareGraph
 
-def randomGraph(n,edges):
+def randomGraph(n):
+	edges=input("No. of edges:")
 	UGraph = snap.GenRndGnm(snap.PUNGraph, n, edges)
 	adj = dict()
 	for x in range(n):
@@ -14,10 +16,12 @@ def randomGraph(n,edges):
 		adj[(i,i)] = 1
 	return adj
 
-N=input("No. of vertices (n<4039):")
-edges=input("No. of edges:")
-adj = randomGraph(N,edges)
-edges = sum([sum(x) for x in adj])/2
+N = input("No. of vertices (n<4039):")
+# adj = randomGraph(N)
+p = 3
+W = 0.5
+adj = UnitSquareGraph(N,p,W).adj
+edges = (sum([val for key, val in adj.iteritems()]) - N)/2
 L = N/10
 
 # declare your variables

### 2016-07-04 unitSquare.py

@@ -1,0 +1,40 @@
+from random import random
+from itertools import combinations
+import networkx as nx
+
+class UnitSquareGraph(object):
+	def __init__(self, N, P, W):
+		self.N = N
+		self.P = P
+		self.W = W
+		points = [[random(),random()] for _ in xrange(self.N)]
+		self.dist = [[None for _ in xrange(self.N)] for _ in xrange(self.N)]
+
+		for i in xrange(self.N):
+			for j in xrange(self.N):
+				self.dist[i][j] = self.dist[j][i] = self.lpNorm(points[i], points[j], self.P)
+
+		self.adj = self.getAdj()
+		self.nxGraph = self.NXify()
+
+	def lpNorm(self,A,B,p):
+		x1, y1 = A
+		x2, y2 = B
+		return ((abs(x2 - x1)**p + abs(y2 - y1)**p)**(1.00/p))
+
+	def getAdj(self):
+		adj = dict()
+		for i in xrange(self.N):
+			for j in xrange(self.N):
+				adj[(i,j)] = adj[(j,i)] = self.dist[i][j] <= self.W
+
+		return adj
+
+	def NXify(self):
+		G = nx.Graph()
+		G.add_nodes_from([x for x in xrange(self.N)])
+		for i in xrange(self.N):
+			for j in xrange(i,self.N):
+				if self.adj[(i,j)]:
+					G.add_edge(i,j)
+		return G

### 2016-07-04 LocalSearchAlgorithm/ls.py
Analysis of Local Search Algorithm

@@ -93,34 +93,36 @@ def doOneSwaps(G, S, L):
 		Vmax = getVmax(G, S, L)
 	return S
 
-N, M = 10,30
-adj = randomGraph(N,M)
-k, L = 5,3
-G = getGraph(N,adj)
-S = getS(G,k)
-S = doOneSwaps(G, S, L)
-H = defaultdict(list)
-#max flow value cannot be greater than the number of nodes in the graph or set V
-if nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't') == N:
-	_,flows = nx.maximum_flow(getFlowGraph(G, S, L), 's', 't')
-	edges = set(G.edges())
-        #if a flow exists along a particular path assigning v to that vertex in S
-	for v in G.nodes():
-		for s in S:
-			if (min(v,s),max(v,s)) in edges:
-				unitflow = False
-				try:
-					if flows[max(v,s + N)][min(v,s + N)] == 1:
-						unitflow = True
-				except KeyError:
+def main(N,adj,k,L):
+	G = getGraph(N,adj)
+	S = getS(G,k)
+	S = doOneSwaps(G, S, L)
+	H = defaultdict(list)
+	result = None
+	#max flow value cannot be greater than the number of nodes in the graph or set V
+	if nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't') == N:
+		'''_,flows = nx.maximum_flow(getFlowGraph(G, S, L), 's', 't')
+		edges = set(G.edges())
+	        #if a flow exists along a particular path assigning v to that vertex in S
+		for v in G.nodes():
+			for s in S:
+				if (min(v,s),max(v,s)) in edges:
+					unitflow = False
 					try:
-						if flows[min(v,s + N)][max(v,s + N)] == 1:
+						if flows[max(v,s + N)][min(v,s + N)] == 1:
 							unitflow = True
 					except KeyError:
-						pass
-				if unitflow:
-					H[s].append(v)
-else:
-	print "Failed!"
-print S
-print H
+						try:
+							if flows[min(v,s + N)][max(v,s + N)] == 1:
+								unitflow = True
+						except KeyError:
+							pass
+					if unitflow:
+						H[s].append(v)'''
+		result = 'Success'
+	else:
+		result = 'Failed'
+	return result
+
+if __name__ == '__main__':
+	main()

### 2016-07-04 OPTIMAL1.py

@@ -1,6 +1,8 @@
 import snap
 from pulp import *
 from unitSquare import UnitSquareGraph
+from random import randint, uniform
+from LocalSearchAlgorithm.ls import main as localSearch
 
 def randomGraph(n):
 	edges=input("No. of edges:")
@@ -16,57 +18,83 @@ def randomGraph(n):
 		adj[(i,i)] = 1
 	return adj
 
-N = input("No. of vertices (n<4039):")
-# adj = randomGraph(N)
-p = 3
-W = 0.5
-adj = UnitSquareGraph(N,p,W).adj
-edges = (sum([val for key, val in adj.iteritems()]) - N)/2
-L = N/10
+def integerProgram(N,p,W):
+	# adj = randomGraph(N)
+	adj = UnitSquareGraph(N,p,W).adj
+	edges = (sum([val for key, val in adj.iteritems()]) - N)/2
+	L = N/10
 
-# declare your variables
-cen = dict(zip([i for i in range(N)],[0 for i in range(N)]))		
-cen = LpVariable.dicts("cen",cen, 0, 1,LpInteger)
+	# declare your variables
+	cen = dict(zip([i for i in range(N)],[0 for i in range(N)]))		
+	cen = LpVariable.dicts("cen",cen, 0, 1,LpInteger)
 
-assignments = {}
-for i in range(N):
-	for j in range(N):
-		assignments[(i,j)] = adj[(i,j)]
+	assignments = {}
+	for i in range(N):
+		for j in range(N):
+			assignments[(i,j)] = adj[(i,j)]
 
-assignments = LpVariable.dicts("assignments",assignments,0,1)
+	assignments = LpVariable.dicts("assignments",assignments,0,1)
 
-# defines the problem
-prob = LpProblem("problem", LpMinimize)
+	# defines the problem
+	prob = LpProblem("problem", LpMinimize)
 
-# defines the objective function to minimize : sum(y)
-prob += lpSum([cen[i] for i in range(N)])
+	# defines the objective function to minimize : sum(y)
+	prob += lpSum([cen[i] for i in range(N)])
 
-############# Constraint definitions ###################
+	############# Constraint definitions ###################
 
-# sum(x_ij) <= L*y[i]
-for i in xrange(N):
[…]

### 2016-07-04 unitSquare.py

@@ -1,5 +1,4 @@
 from random import random
-from itertools import combinations
 import networkx as nx
 
 class UnitSquareGraph(object):

### 2016-07-04 paper.tex
Update paper.tex

@@
 Thus, if we say there are p partitions then $\sum_{i=1}^{p}\lceil (C_i-B(C_i))/L\rceil$ vertices are required atleast to cover the graph and hence this comes to be a lower bound.
-
- This has been presented in a research paper already but the fact that we are not really involving the boundary vertices did not sink in and though it did not work out but we toyed for some time with ideas of somehow involving the boundary vertices.
+\\\\This has been presented in a research paper already but the fact that we are not really involving the boundary vertices did not sink in and though it did not work out but we toyed for some time with ideas of somehow involving the boundary vertices.
 We thought with the current vertices the remaining capacity i.e.
@@
 Through this we can decide opening more centers or shifting the centers so as to cover more boundary vertice.
-But it always depends upon the connectivity of the particular graph and what kind of partition we take and that was where we left this.
-\subsection{Our Attempts}
+But it always depends upon the connectivity of the particular graph and what kind of partition we take and that was where we left this.\\ Later when Jatin and Aounon started thinking towards this way we further applied our thinking on the same.
+
+Lets say we partition the graph into sets of nodes $C_i \: 1 \leq i \leq N$:
+\begin{figure}
+%partitioned figure
+\end{figure}
+As discussed before, the minimum number of centers we need to place inside the partition $C_i$ is $\lceil ((C_i-B(C_i))/L) \rceil$.
+The residual capacity, which can cover boundary vertices as mentioned above is,$\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$ , which we can use to cover the boundary vertices.
+\\\\
+To do this, a flow network is created:
+\begin{figure}
+%flow figure for partitions and boundary vertices
+\end{figure}\\
+Now there are two cases:
+\begin{itemize}
+\item If we are not able to find a flow to cover all the boundary vertices with the residual capacities, then there exist a set of partitions $P_1, P_2,\ldots P_i$ and $B(P_1), B(P_2),\ldots B(P_i)$ for which Hall’s theorem doesnt hold i.e.:
+ $$|B|> {\sum_{i=1}^{N}\lceil (P_i-B(P_i))/L\rceil*L-(P_i-B(P_i))}$$
+which after rearrangement becomes:\\
+$$\lceil (\sum_{i=1}^{N}P_i)/L \rceil > \sum_{i=1}^{N} \lceil P_i/L \rceil   $$
+This in turn means we can merge the above set of partitions to get a better lower bound. The boundary vertices form the interior of the new set of partitions. 
+\item If the flow exists, this is where we are stuck again.
+We do not know if there is such a set of centers we can choose such that we can make use of enough residual flow required and actually taken into account by the flow network.
+Our attempt to resolve this:
+\begin{figure}
+%<draw diagram as in the  notebook, day 29>. 
+\end{figure}
+We define
+\begin{itemize}
+
+\item Node ‘a’ : A center which does not have edge to any boundary vertex.
+\item Node ‘b’ : An interior non - center, which is a client of ‘a’ and adjacent to a boundary vertex. We will call it the semi boundary vertex. 
+\end{itemize} 
+We observe that if we make as many semi-boundary centers as possible, such that they cover maximum number of boundary vertices, by switching the centers from 'a' to 'b' then we can come to a conclusion.
+If we make the semi-boundary vertex ‘b’ as a center, then it will cover all the clients that have been covered by ‘a’, but its minimum maximum distance would be 4*OPT.
+Also, we would need to shift to such a set of semi-boundary vertices that maximises the number of distinct boundary vertices getting covered.
+
+So, we make a flow network:
+\begin{figure}
+%<diagram of potential semi boundary vertices and existing vertices>
+\end{figure}
+That is, we cannot make greedy moves and just move to the semi-boundary vertices with maximum boundary neighbors.
+As it is equally necessary to make sure these boundary neighbours are distinct.
+To ensure this, we create the following flow network:
+\begin{figure}
+%<diagram of the complete flow network>
+\end{figure}
+But we realised that this problem of covering maximum number of boundary vertices will eventually be comparable to the max-coverage problem, which is NP-hard.The comparison is made by taking the nodes inside the partition as the subsets and the universe outside.
+If there is a way where we can get minimum subsets to cover all of the universe then it is the same solution.
+Since it is NP-hard we know this won't be possible.
+
+ However, we still feel that this idea of semi-boundary vertices could lead to some result. 
+\end{itemize}
+\subsection{Our Attempt}
 \begin{itemize}
@@
 \\\\\textbf{Theorem:}
-When there can be no more edge reassignments, then no center at level l, has an edge of length <= 4 to any node in level l’ >= l+2 for all l. 
+When there can be no more edge reassignments, then no center at level l, has an edge of length $\leq 4$ to any node in level $l’ \geq l+2$ for all l. 
 \\\\

### 2016-07-04 LocalSearchAlgorithm/ls.py
Achieved > 98% accuracy by fixing bugs

@@ -2,6 +2,8 @@ import networkx as nx
 import snap
 from random import shuffle
 from collections import defaultdict
+import matplotlib.pyplot as plt
+import pprint
 
 #Generating a random graph using snap
 def randomGraph(n,edges):
@@ -43,9 +45,9 @@ def getFlowGraph(G, S, L):
 	N = len(G.nodes())
 	#for common nodes in V and S make separate keys for S
 	for x in G.nodes():
-		FG.add_node(x)
 		if x in S:
 			FG.add_node(x + N)
+		FG.add_node(x)
 
 	FG.add_nodes_from(['s','t'])
 	edges = set(G.edges())
@@ -87,41 +89,51 @@ def getVmax(G, S, L):
 
 #changing S and Vmax by one swaps so as to achieve the max flow possible after each obtained S
 def doOneSwaps(G, S, L):
-	Vmax = getVmax(G, S, L)
+	Vmax = getVmax(G, S[:], L)
 	while nx.maximum_flow_value(getFlowGraph(G, Vmax, L), 's', 't') > nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't'):
 		S = Vmax
-		Vmax = getVmax(G, S, L)
+		Vmax = getVmax(G, S[:], L)
+	#print nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't')
 	return S
 
 def main(N,adj,k,L):
-	G = getGraph(N,adj)
-	S = getS(G,k)
-	S = doOneSwaps(G, S, L)
-	H = defaultdict(list)
-	result = None
-	#max flow value cannot be greater than the number of nodes in the graph or set V
-	if nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't') == N:
-		'''_,flows = nx.maximum_flow(getFlowGraph(G, S, L), 's', 't')
-		edges = set(G.edges())
-	        #if a flow exists along a particular path assigning v to that vertex in S
-		for v in G.nodes():
-			for s in S:
-				if (min(v,s),max(v,s)) in edges:
-					unitflow = False
-					try:
-						if flows[max(v,s + N)][min(v,s + N)] == 1:
-							unitflow = True
-					except KeyError:
+	iterations = 5
+	result = 'Failed'
+	while iterations > 0 and result == 'Failed':
+		G = getGraph(N,adj)
+		S = getS(G,k)
+		S = doOneSwaps(G, S, L)
+		H = defaultdict(list)
+		result = None
[…]

### 2016-07-04 OPTIMAL1.py

@@ -92,7 +92,7 @@ def main():
 				res.append(result)
 			p <<= 1
 	except KeyboardInterrupt:
-		pass
+		raise
 	with open('results','w') as f:
 		f.write('\n'.join(res))
 

### 2016-07-05 LocalSearchAlgorithm/ls_orig.py
Added counter examples and randomization

@@ -1,6 +1,6 @@
 import networkx as nx
 import snap
-from random import shuffle, randint, choice
+from random import shuffle, randint
 from collections import defaultdict
 import matplotlib.pyplot as plt
 import pprint, pickle
@@ -67,24 +67,23 @@ def getVmax(G, S, L):
 	# flow[i][j] = max-flow in (S, V) when S[i] is swapped with V[j]
 	flow = [[None for _ in xrange(len(V))] for _ in xrange(len(S))]
 	setS = set(S)
-	without_swap_flow = nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't')
 	for i in xrange(len(S)):
 		for j in xrange(len(V)):
 			if V[j] not in setS:
 				temp = S[i]
 				S[i] = V[j]
 				flow_graph = getFlowGraph(G, S, L)
-				flow[i][j] = nx.maximum_flow_value(flow_graph, 's', 't') > without_swap_flow
+				flow[i][j] = nx.maximum_flow_value(flow_graph, 's', 't')
 				S[i] = temp
 
-	swap_pair = []
+	max_value = 0
+	swap_pair = None
 	for i in xrange(len(S)):
 		for j in xrange(len(V)):
-			if flow[i][j]:
-				swap_pair.append([i,j])
-	if swap_pair:
-		i,j = choice(swap_pair)
-	else: return S
+			if max_value < flow[i][j]:
+				swap_pair = (i,j)
+				max_value = flow[i][j]
+	i,j = swap_pair
 	S[i] = V[j]
 	return S
 
@@ -130,8 +129,8 @@ def main(N,adj,k,L):
 		else:
 			result = 'Failed'
 		iterations -= 1
-	if result == 'Failed' and N <= 50:
-		pos = nx.spring_layout(G,k=0.5)
+	if result == 'Failed' and N <= 30:
+		pos = nx.spring_layout(G)
 		nx.draw_networkx_nodes(G, pos, nodelist=S, node_color='b', node_size=200)
 		nx.draw_networkx_nodes(G, pos, nodelist=list(set(G.nodes()) - set(S)), node_color='r', node_size=200)
 		nx.draw_networkx_edges(G, pos, edgeList=list(G.edges()))

### 2016-07-05 OPTIMAL1.py

@@ -1,8 +1,9 @@
-import snap
+import snap, os
 from pulp import *
 from unitSquare import UnitSquareGraph
 from random import randint, uniform
 from LocalSearchAlgorithm.ls import main as localSearch
+from pickle import load
 
 def randomGraph(n):
 	edges=input("No. of edges:")
@@ -18,9 +19,10 @@ def randomGraph(n):
 		adj[(i,i)] = 1
 	return adj
 
-def integerProgram(N,p,W):
+def integerProgram(N,adj=None,p=None,W=None):
 	# adj = randomGraph(N)
-	adj = UnitSquareGraph(N,p,W).adj
+	if not adj: 
+		adj = UnitSquareGraph(N,p,W).adj
 	edges = (sum([val for key, val in adj.iteritems()]) - N)/2
 	L = N/10
 
@@ -71,13 +73,36 @@ def integerProgram(N,p,W):
 	result = '{}\t{}\t{}\t{}'.format(N,edges, LpStatus[prob.status], count)
 	return result, adj
 
+def test_counter_cases():
+	header = '\t'.join(['Nodes','Edges','Status','K','Local Search'])
+	print header
+	res = []
+	try:
+		for fname in os.listdir('failures/test'):
+			if not fname.endswith('.png'):
+				adj = load(open('failures/test/' + fname,'r'))
+				N = len(adj)
+				a = dict()
+				for i in xrange(len(adj)):
+					for j in xrange(len(adj)):
+						a[(i,j)] = a[(j,i)] = adj[i][j]
+				opt, adj = integerProgram(N,a)
+				ls = localSearch(N,adj,int(opt.split('\t')[-1]),N/10)
+				result = opt + '\t' + ls
+				print result
+				res.append(result)
+	except KeyboardInterrupt:
+		pass
+	with open('results','w') as f:
+		f.write('\n'.join(res))
+	
 def main():
 	header = '\t'.join(['Nodes','Edges','Status','K','P','Local Search'])
 	print header
 	p = 1
 	RAND_GRAPH_COUNT = 10
 	P_LIMIT = 1 << 10
-	NODE_LIMIT = 80
+	NODE_LIMIT = 40
 	W_LOW, W_HIGH = 0.2, 0.4
 	res = [header]
 	try:
@@ -85,14 +110,14 @@ def main():
 			for _ in xrange(RAND_GRAPH_COUNT):
 				N = randint(20,NODE_LIMIT)
[…]

### 2016-07-06 LocalSearchAlgorithm/ls.py
Analysis with failures

@@ -1,9 +1,10 @@
 import networkx as nx
 import snap
-from random import shuffle, randint, choice
+from random import shuffle, randint
 from collections import defaultdict
 import matplotlib.pyplot as plt
 import pprint, pickle
+from ls_random import main as randomizedLS
 
 #Generating a random graph using snap
 def randomGraph(n,edges):
@@ -67,24 +68,23 @@ def getVmax(G, S, L):
 	# flow[i][j] = max-flow in (S, V) when S[i] is swapped with V[j]
 	flow = [[None for _ in xrange(len(V))] for _ in xrange(len(S))]
 	setS = set(S)
-	without_swap_flow = nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't')
 	for i in xrange(len(S)):
 		for j in xrange(len(V)):
 			if V[j] not in setS:
 				temp = S[i]
 				S[i] = V[j]
 				flow_graph = getFlowGraph(G, S, L)
-				flow[i][j] = nx.maximum_flow_value(flow_graph, 's', 't') > without_swap_flow
+				flow[i][j] = nx.maximum_flow_value(flow_graph, 's', 't')
 				S[i] = temp
 
-	swap_pair = []
+	max_value = 0
+	swap_pair = None
 	for i in xrange(len(S)):
 		for j in xrange(len(V)):
-			if flow[i][j]:
-				swap_pair.append([i,j])
-	if swap_pair:
-		i,j = choice(swap_pair)
-	else: return S
+			if max_value < flow[i][j]:
+				swap_pair = (i,j)
+				max_value = flow[i][j]
+	i,j = swap_pair
 	S[i] = V[j]
 	return S
 
@@ -98,9 +98,10 @@ def doOneSwaps(G, S, L):
 	return S
 
 def main(N,adj,k,L):
-	iterations = 5
+	iterations = 10
 	result = 'Failed'
 	while iterations > 0 and result == 'Failed':
+		print iterations
 		G = getGraph(N,adj)
 		S = getS(G,k)
 		S = doOneSwaps(G, S, L)
@@ -130,8 +131,10 @@ def main(N,adj,k,L):
 		else:
 			result = 'Failed'
 		iterations -= 1
-	if result == 'Failed' and N <= 50:
-		pos = nx.spring_layout(G,k=0.5)
+	if result == 'Failed':
+		result = randomizedLS(N, adj, k, L)
[…]

### 2016-07-06 LocalSearchAlgorithm/ls_random.py

@@ -1,6 +1,6 @@
 import networkx as nx
 import snap
-from random import shuffle, randint
+from random import shuffle, randint, choice
 from collections import defaultdict
 import matplotlib.pyplot as plt
 import pprint, pickle
@@ -67,23 +67,24 @@ def getVmax(G, S, L):
 	# flow[i][j] = max-flow in (S, V) when S[i] is swapped with V[j]
 	flow = [[None for _ in xrange(len(V))] for _ in xrange(len(S))]
 	setS = set(S)
+	without_swap_flow = nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't')
 	for i in xrange(len(S)):
 		for j in xrange(len(V)):
 			if V[j] not in setS:
 				temp = S[i]
 				S[i] = V[j]
 				flow_graph = getFlowGraph(G, S, L)
-				flow[i][j] = nx.maximum_flow_value(flow_graph, 's', 't')
+				flow[i][j] = nx.maximum_flow_value(flow_graph, 's', 't') > without_swap_flow
 				S[i] = temp
 
-	max_value = 0
-	swap_pair = None
+	swap_pair = []
 	for i in xrange(len(S)):
 		for j in xrange(len(V)):
-			if max_value < flow[i][j]:
-				swap_pair = (i,j)
-				max_value = flow[i][j]
-	i,j = swap_pair
+			swap_pair.append([i,j])
+
+	if swap_pair:
+		i,j = choice(swap_pair)
+	else: return S
 	S[i] = V[j]
 	return S
 
@@ -97,9 +98,10 @@ def doOneSwaps(G, S, L):
 	return S
 
 def main(N,adj,k,L):
-	iterations = 5
+	iterations = 10
 	result = 'Failed'
 	while iterations > 0 and result == 'Failed':
+		print iterations
 		G = getGraph(N,adj)
 		S = getS(G,k)
 		S = doOneSwaps(G, S, L)
@@ -129,8 +131,8 @@ def main(N,adj,k,L):
 		else:
 			result = 'Failed'
 		iterations -= 1
-	if result == 'Failed' and N <= 30:
-		pos = nx.spring_layout(G)
+	'''if result == 'Failed' and N <= 50:
+		pos = nx.spring_layout(G,k=0.5)
 		nx.draw_networkx_nodes(G, pos, nodelist=S, node_color='b', node_size=200)
[…]

### 2016-07-06 OPTIMAL1.py

@@ -3,7 +3,9 @@ from pulp import *
 from unitSquare import UnitSquareGraph
 from random import randint, uniform
 from LocalSearchAlgorithm.ls import main as localSearch
-from pickle import load
+from pickle import load, dump
+import networkx as nx
+import matplotlib.pyplot as plt
 
 def randomGraph(n):
 	edges=input("No. of edges:")
@@ -112,7 +114,7 @@ def main():
 				W = uniform(W_LOW, W_HIGH)
 				opt, adj = integerProgram(N,dict(),p,W)
 				ls = localSearch(N,adj,int(opt.split('\t')[-1]),N/10)
-				result = opt + '\t' + str(p) + '\t' + ls
+				result = '\t'.join(opt, str(p), ls)
 				print result
 				res.append(result)
 			p <<= 1
@@ -122,4 +124,4 @@ def main():
 		f.write('\n'.join(res))
 
 if __name__ == '__main__':
-	main()
+	test_counter_cases()

### 2016-07-07 Capacitated K-Center.tex
Report up till now
Add files via upload

--- 2016-07-04 paper.tex
@@
 \usepackage{float}
+\usepackage{color}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=black,
+    urlcolor=red,
+    linktoc=all
+}
+\usepackage[toc,page]{appendix}
 
+\addtocontents{toc}{\protect\hypertarget{toc}{}}
 \usepackage{algorithmic}
@@
 
-\author{Anya Chaturvedi \\ Ketaki Vaidya \and K. R. Prajwal \\ Sagar Sahni  }
-\title{Summer Report On The Capacitated K-Center Problem}
+\author{Anya Chaturvedi \\ Sagar Sahni \and K. R. Prajwal \\ Ketaki Vaidya  }
+\title{%
+  The Capacitated K-Center Problem\\
+  \large Summer Internship Report 
+  ($9^{th} May-8^{th} July$)}
+ \date{}
 \begin{document}
+\begin{titlepage}
+
+\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
+
+\center
+
+%\textsc{\LARGE Capacitated K-Center Problem}\\[1.5cm] % Name of your university/college
+\textsc{\Large Summer Internship}\\[0.5cm] % Major heading such as course name
+\textsc{\large Indian Institute of Technology, Delhi}\\[0.5cm] % Minor heading such as course title
+
+\HRule \\[0.4cm]
+{ \huge \bfseries Capacitated K-Center Problem}\\[0.4cm] % Title of your document
+\HRule \\[1.5cm]
+
+%----------------------------------------------------------------------------------------
+%   AUTHOR SECTION
+%----------------------------------------------------------------------------------------
+
+\includegraphics[scale=0.06]{iitd_logo.png}\\[1cm] % Include a department/university logo - this will require the graphicx package
+
+{\large May $9^{th}$ - July $8^{th}$}\\[9cm] % Date, change the \today to a set date if you want to be precise
+
+%----------------------------------------------------------------------------------------
+%   LOGO SECTION
+%----------------------------------------------------------------------------------------
+
+ \begin{minipage}{0.4\textwidth}
+\begin{flushleft} \large
+\emph{\\Authors:}\\
+Anya Chaturvedi\\
+K.R. Prajwal\\
+Sagar Sahni\\
+Ketaki Vaidya
+ % Your name
+\end{flushleft}
+\end{minipage}
+~
+\begin{minipage}{0.4\textwidth}
+\begin{flushright} \large
+\emph{Supervisor:} \\
+Dr. Naveen Garg \\
+Professor\\
+Dept. of CSE\\
+IIT Delhi % Supervisor's Name
+\end{flushright}
+\end{minipage}\\[2cm]
+%----------------------------------------------------------------------------------------
+
+\vfill % Fill the rest of the page with whitespace
+
+\end{titlepage}
 \maketitle
-\section{Introduction to our Problem}
-The capacitated K-center problem is basically a facility location problem, where one is asked to locate K facilities in a graph and to assign vertices to these facilities. In doing this we minimize
-the maximum distance from a vertex to the facility to which it is assigned while keeping in mind that each facility may be assigned at most L vertices including itself.
+\tableofcontents
+%\section[Abstract]{Abstract \begin{flushright}\hyperlink{toc}{TOC}\end{flushright}}
+\section{Abstract}
+The capacitated $K$-center problem is basically a facility location problem, where one is asked to assign $K$ points to $K$ facilities in a given distance metric. In doing this we minimize
+the maximum distance from a vertex to the facility to which it is assigned while keeping in mind that each facility may be assigned at most $L$ vertices including itself.
 This problem is known to be NP-hard.
 
-We show our attempts at solving this problem, counter examples as learnt by us and few basic implementations of the same.
-The implementations include finding the optimal using the integer program and a partially accurate local search algorithm.
-\section{A Look At The K-center problem}
-The problem taken up by us is actually a generalization of the K-center problem which we will explain here.
-Given n vertices with specified distances, one wants to build k facilities at different vertices and minimize the maximum distance of a vertex to a facility.
+We show our attempts at solving this problem, counter examples as learnt by us and a few basic implementations of the same.
+Starting by a more formal description of our problem, we describe the flow method which helps us verify a solution to the problem.
+Next, we implemented the integer program and a partially correct local search algorithm.
+In implementing the above programs we have used three ways for making the input graphs.
+One is a random graph, second a more clustered form i.e.
+a star graph and the last one is generated by taking points in a unit square.
+Other than this we have included a few observations which may not be much conclusive but are our attempts on solving the problem during the summer.
+\section{A Look at the Problem}
+The problem taken up by us is actually a generalization of the $K$-center problem which we will explain here. 
+\subsection{The $K$-Center Problem}
+Given n vertices with specified distances, one wants to build $K$ facilities at different vertices such that each vertex has access to a facility and minimize the maximum distance between the vertex and the corresponding facility.
 This problem is NP-hard.
-An approximation algorithm with a factor of $\eta$ ,for a minimization problem,is
-a polynomial time algorithm that guarantees a solution with cost at most $\eta$ times the cost of an optimal solution.
-For the basic K-center methods have been presented for obtaining an approximation factor of 2.
-Given a complete undirected graph G = (V, E) with distances $d(v_i, v_j) \in N$ satisfying the triangle inequality, find a subset $S \subseteq V$ with $|S| = k$.\\\\
- \textbf{Input:}\\1. The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2. An
-upper bound on the number of centers K.\\\\
+An approximation algorithm with a factor of $\eta$ ,for a minimization problem,is a polynomial time algorithm that guarantees a solution with cost at most $\eta$ times the cost of an optimal solution.
+For the basic $K$-center, methods have been presented for obtaining an approximation factor of 2.
+Given a complete undirected graph G = (V, E) with distances $d(v_i, v_j) \in N$ satisfying the triangle inequality, we have to find a subset $S \subseteq V$ such that $|S| = k$ and covering all $V$.\\\\
+ \textbf{Input:}\\1. The vertices must be in a metric space, or in other words IN a complete graph that satisfies the triangle inequality.\\2. An upper bound on the number of centers K.\\\\
 \textbf{Formal Definition:}\\
@@
 
-This is much similar to the problem of placing k disks such that all points are covered in the set V and thus finding the minimum radius for the disks.
+This is much similar to the problem of placing k disks such that all points are covered in the set V and thus finding the minimising the maximum radius for the disks.
 %\begin{center}
@@
 %\end{center}
-\section{The Capacitated K-Center}
+\subsection{The Capacitated K-Center}
 The capacitated K-center problem is nothing but a generalization of the K-center problem. We have to
@@
 \textbf{Input:}\\1. The vertices must be in a metric space, or in other words a complete graph that satisfies the triangle inequality.\\2. An
-upper bound on the number of centers K.\\3. A maximum load L.\\\\
+upper bound on the number of centers, K.\\3. A maximum capacity for each center, L.\\\\
 \textbf{Formal Definition:}\\
@@
 Later a 6-approximation was found which is the best up till date while a 5-approximation works when we can assign multiple centers at a single vertex without including the vertex in L.
-This was our problem for the summer.
 
-Initially we went through the 2.6 and 9.3 sections of Williamson Schmoy which solve the min degree spanning tree problem which is also NP-hard and got to know of methods like local search used to create approximation algorithms.
+Initially we went through the 2.6 and 9.3 sections of Williamson Schmoy which solve the problem of finding the min degree spanning tree problem which is also NP-hard and got to know of methods like local search used to create approximation algorithms.
 
@@
 We can easily set up such an equivalence if we slightly modify our problem.
-Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$, $S \subseteq V$ is a capacitated dominating set if there exists a mapping $f : V \backslash S \rightarrow S$ (domination mapping) such that:\begin{enumerate}
+Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$ and $S \subseteq V$ is a capacitated dominating set if there exists a mapping $f : V \rightarrow S$ (domination mapping) such that:\begin{enumerate}
 
-\item $\forall v \in V \backslash S,\forall s \in S,f(v) = s \Longrightarrow (v,s) \in E$\\ \item $\forall s \in S,| \{ v \in V \backslash S | f(v) = s \} | \leq c(s)$
+\item $\forall v \in V ,\forall s \in S,f(v) = s \Longrightarrow (v,s) \in E$\\ \item $\forall s \in S,| \{ v \in V \backslash S | f(v) = s \} | \leq c(s)$
 \end{enumerate}In the new version of the k-center problem, the goal is to get a set S of k vertices and an assignment $h : V \backslash S \rightarrow S$ of every vertex (in $V \backslash S$) to an open center such that the longest distance between a vertex and a center it is assigned to is minimum and no facility is assigned more vertices than its capacity.
@@
 \\
-\begin{center}
+The flow network as described has been shown in the figure:
+\begin{flushleft}
  \begin{figure}[H]
  \begin{center}
- \includegraphics[scale=1]{flow.png}
+ \includegraphics[scale=0.55]{diag2.jpg}
  \end{center}
@@
 \end{figure}
- \end{center} Now it is easy to verify that, S is a capacitated dominating set in G if and only if $G_S$ has a maximum coverage of $|V \backslash S|$ from s to t equal to the total vertices in the graph.
+\end{flushleft}
+  Now it is easy to verify that, S is a capacitated dominating set in G if and only if $G_S$ has a maximum coverage of $|V \backslash S|$ from s to t equal to the total vertices in the graph.
 
@@
 
-\begin{center}
-
-\begin{figure}[H]
- \includegraphics[scale=1]{1.png}
-  \caption{Code}
-  \label{Figure 2}
-\end{figure}
-
-\begin{figure}[H]
- \includegraphics[scale=1]{2.png}
-  \caption{Code}
-  \label{Figure 3}
-\end{figure}
-\end{center}
 \textbf{Objective Function:}\\
@@
 
+You can refer to the code in Appendix A.
+
 \section{Local Search Algorithm}
@@
 If the optimum set dominates more vertices than S then we set S to that set and continue the process till we have reached a local optima.
-We do the assignments through a network flow graph.\\\\
+We do the assignments through a network flow graph.\\\\\\
 \textbf{Algorithm:}
@@
 
+You can refer to the code in Appendix B.
+
+\section{Graph Generation}
+\subsection{Random Graph}
+For testing the implemented algorithms on random graphs, SNAP, a Python based system developed by Stanford University was used which takes the number of nodes and edges as input and gives a random subgraph of a data set and represent it as an adjacency matrix, ready to be fed into the LP and local search algorithm.
+
+You can refer to the code in Appendix C.
+
+\subsection{Star Graph}
+In an attempt to try our programs on a more clustered data set, this program was implemented to create sparsely-connected star graphs, with edges chosen to be added with a probability p.
+
+You can refer to the code in Appendix D.
+
+\subsection{Unit Square}
+On discussing our above mentioned methods with Sir he suggested another way for making the input graphs which he felt might give us better  results for further analysis. 
+The method proceeds by taking N random points in a unit square.
+Calculate the edge weight between all possible pairs of these $N$ points by using different $L^p$ norms, for $p \geq 1$.
+Choose a $W$, to denote the maximum edge weight allowed in a particular graph which reduces the edges in the otherwise obtained complete graph. 
+Build the graph, with the $N$ random points as nodes and add edges $(a,b)$ if distance between $(a,b)$ is $\leq W$, for all $a,b$ $\in$ $N$. 
+Use this graph to obtain the optimal $K$ using a capacity, which we have taken as $L = N/10$.
+Use the same graph to check if the randomized local search algorithm yields the optimal solution with the above obtained $K$ and $L$.
+
+Even though this did not strike at first on why this will be in any manner be different than using random graphs, still we decided to proceed with the implementation.
+During our visualization of the graphs created, we saw that this method gave us a very large variety of graphs, in the sense that the graphs had local clusters, articulation points, isolated vertices, cliques and a wide variation in the degrees of the nodes.
+
+You can refer to the code in Appendix E.
+\section{Observations made}
+This section is a collection of all our trials and errors during our exploration of this topic along with few of the concepts learnt which provide the base for these trials.
+\subsection{Lower Bound on K}
+Lets say we make disjoint set of partitions of our input graph nodes such that each partition has two types of vertices.
+Inner and boundary, the inner vertices are the ones which have no edges outside its partition, while the boundary vertices are vertices which do have edges to other partitions.
+Let the $i^{th}$ partition be represented by its inner vertices $C_i$ and its boundary vertices as $B(C_i)$.
+
+Since we know K vertices can cover up to L vertices so the max vertices than can be covered is $V = K*L$.
+Hence the minimum $K$ required to cover $V$ vertices is $\lceil V/L\rceil$.
+This is a naive lower bound on $K$.
+But using this concept, we can get a better lower bound.
+
+Here, in the partitioning as described above, for the vertices other than the boundary vertices we can say that they can only be covered by vertices of their own partition thus we need to open centers in the partition itself for such vertices.
+Thus, if we say there are $p$ partitions then $\sum_{i=1}^{p}\lceil (C_i-B(C_i))/L\rceil$ vertices are required atleast to cover the graph and hence this comes to be a lower bound.
+\\\\The above bound has been presented in a research paper already.
+We observed that, the above mentioned paper is not involving the boundary vertices in formulating a lower bound.
+So, we toyed for some time with ideas on involving the boundary vertices.
+We thought using the residual capacity, i.e.
+$\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$ we may be able to cover some or even all of the boundary vertices.
+Through this we can decide opening more centers or shifting the centers so as to cover more boundary vertices.
+But all of this depends upon the connectivity of the particular graph and what kind of partition we take which did not look promising after a point of time either.\\ Later when Jatin and Aounon started thinking towards this way we again applied our thinking on the same.
+
+Lets say we partition the graph into sets of nodes $C_i \: 1 \leq i \leq N$:
+
+\begin{flushright}
 \begin{figure}[H]
- \includegraphics[scale=1]{a.png}
-  \caption{Code}
-  \label{Figure 4}
+\includegraphics[scale=0.2]{diag7.jpg}
+\caption{Partitioning the Vertex Set}
+\end{figure}
+\end{flushright}
+
+As discussed before, the minimum number of centers we need to place inside the partition $C_i$ is $\lceil ((C_i-B(C_i))/L) \rceil$.
+The residual capacity, which can cover boundary vertices as mentioned above is,$\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$ , can be used to cover the boundary vertices.
+\\\\
+To do this, a flow network is created:
+
+\begin{center}
+\begin{figure}[H]
+\includegraphics[scale=0.55]{diag1.jpg}
+\caption{$Z=\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$}
+\end{figure}
+\end{center}
+Here $Z$ refers to the remaining capacity of the centers as put in the inner vertices i.e $\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$.
+Now there are two cases:
+\begin{itemize}
+\item If we are not able to find a flow to cover all the boundary vertices within a distance of 2 with the residual capacities, then there exist a set of partitions $P_1, P_2,\ldots P_i$ and $B(P_1), B(P_2),\ldots B(P_i)$ for which Hall’s theorem does not hold i.e.:
+ $$|B|> {\sum_{i=1}^{N}\lceil (P_i-B(P_i))/L\rceil*L-(P_i-B(P_i))}$$
+which after rearrangement becomes:\\
+$$\lceil (\sum_{i=1}^{N}P_i)/L \rceil > \sum_{i=1}^{N} \lceil P_i/L \rceil   $$
+This, in turn, means we can merge the above set of partitions to get a better lower bound.
+The boundary vertices will always be in the interior of the new set of partitions, because if they were not then it can be covered by a residual capacity, a contradiction.
+
+\item If the flow exists, this is where we are stuck again.
+We do not know if there is such a set of centers we can choose such that we can make use of all the necessary residual capacity which is actually taken into account by the flow network.
+Our attempt to resolve this:
+
+\begin{flushleft}
+\begin{figure}[H]
+\includegraphics[scale=0.8]{anya.jpg}
+
+  \caption{Reassignment of Centers}
+\end{figure}
+\end{flushleft}
+
+We define
+\begin{itemize}
+
+\item Node type: $a$ : A center which does not have edge to any boundary vertex.
+\item Node type: $q$ : An interior non - center, which is a client of $a$ and adjacent to a boundary vertex. We will call it the semi boundary vertex. 
+\end{itemize} 
+We observe that if we make as many semi-boundary centers as possible, such that they cover maximum number of boundary vertices, by shifting the centers located at $a$ to $q$ then we can come to a conclusion.
+If we make the semi-boundary vertex $b$ as a center, then it will cover all the clients that have been covered by its respective center $a$, but now the minimum maximum distance would be at most 4*OPT.
+Also, we would need to shift to such a set of semi-boundary vertices that maximises the number of distinct boundary vertices getting covered.
+
+So, we make a flow network:
+
+\begin{flushleft}
+\begin{figure}[H]
+\includegraphics[scale=0.6]{diag3(2).jpg}
+\caption{Flow to exchange Semi-boundary vertices with Existing Centers}
 \end{figure}
 
+\end{flushleft}
+But we cannot make greedy moves and just move to the semi-boundary vertices with maximum boundary neighbors, as it is very necessary to make sure these boundary neighbours are distinct.
+To ensure this, we modify the above flow network:
+\begin{center}
 \begin{figure}[H]
- \includegraphics[scale=1]{b.png}
-  \caption{Code}
-  \label{Figure 5}
+\includegraphics[scale=0.4]{diag4.jpg}
+\caption{New Flow Method}
 \end{figure}
+We keep the capacity of all edges in this flow network as 1 but modify the edge weights of edge weights between B,Q and A to keep a check.
+Between A and Q, $e_1$ the remaining capacity of $q_i$ which is -- $L-$the number of non centers transferred to it through $a_i$ is taken as the edge weight between $q_i$ and $a_i$.
+While the edge weight between B and Q, $e_2$ is equal to the inverse of the number of boundary vertices that the corresponding q will cover if selected.
+\begin{figure}[H]
+\includegraphics[scale=0.4]{diag6.jpg}
+\caption{Case of 2 Available Paths}
+\end{figure}
+\end{center}
+In a case as shown above in the figure if capacity permits, we will choose $e_2 = 1/8$ as it is covering 7 other boundary vertices except the one in the selected augmented path.
+Also we will have to make changes to the edge weights like converting 1/4 to zero and the corresponding edges of the same semi boundary vertex involved to 1/3 and the semi-boundary to corresponding center as 3.
+If later 1/8 weight wedge is not a part of the max flow then we simply revert back to the original weights.\\
+But we realised that this problem of covering maximum number of boundary vertices is a problem reducible to the max-coverage problem, which is NP-hard.
+Hence the problem we are trying to solve is indeed NP-hard.
+The comparison is made by taking the nodes inside the partition as the subsets and the universe outside.
+\begin{center}
+\begin{figure}[H]
+\includegraphics[scale=0.6]{diag5.jpg}
+\caption{Max-Coverage Problem}
+\end{figure}
+\end{center}
+If there is a way where we can get minimum subsets to cover all of the universe then it is the same solution which is not possible.
 
-\begin{figure}[H]
- \includegraphics[scale=1]{c.png}
-  \caption{Code}
-  \label{Figure 6}
-\end{figure}
-
-\begin{figure}[H]
- \includegraphics[scale=1]{d.png}
-  \caption{Code}
-  \label{Figure 7}
-\end{figure}
-
-\section{Star Graph Generation}
-In an attempt to try our programs on a more clustered data set, this program was implemented such that in this star graphs are formed which are sparsely connected to each other by edges which are added to the graph based on a probability p.
-
-\begin{figure}[H]
- \includegraphics[scale=1]{g1.png}
-  \caption{Code}
-  \label{Figure 8}
-\end{figure}
-
-\begin{figure}[H]
- \includegraphics[scale=1]{g2.png}
-  \caption{Code}
-  \label{Figure 9}
-\end{figure}
-
-\section{Observations made}
-This section basically focuses on all our trials and errors we had during our intern on this topic along with few of the concepts learnt which provide the base for these trials.
-\subsection{Lower Bound on K}
-Lets say we make some partition on our input graph such that each partition has two types of vertices.
-Inner and boundary, the inner vertices are the ones within the particular partition while the boundary vertices are inner vertices which even have edges to other partitions.
-Let the $i^th$ partition be represented by its inner vertice $C_i$ and its boundary vertices as a function of $C_i$ as $B(C_i)$.
-
-Since we know K vertices can cover up to L vertices so the max vertices than can be covered is $V = K*L$.
-Hence K can be taken to be approximately $\lceil V/L\rceil$.
-Thus if we try forming a lower bound so as to claim that the graph requires atleast these many vertices as equal to the bound then it might be of help.
-
-Here, in the partitioning as described above, for the vertices other than the boundary vertices we can say that they can only be covered by vertices of their own partition thus we need to open centers in the partition itself for such vertices.
-Thus, if we say there are p partitions then $\sum_{i=1}^{p}\lceil (C_i-B(C_i))/L\rceil$ vertices are required atleast to cover the graph and hence this comes to be a lower bound.
-
- This has been presented in a research paper already but the fact that we are not really involving the boundary vertices did not sink in and though it did not work out but we toyed for some time with ideas of somehow involving the boundary vertices.
-We thought with the current vertices the remaining capacity i.e.
-$\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$ we may be able to cover some or even all of the boundary vertices.
-Through this we can decide opening more centers or shifting the centers so as to cover more boundary vertice.
-But it always depends upon the connectivity of the particular graph and what kind of partition we take and that was where we left this.
-\subsection{Our Attempts}
+ However, we still feel that this idea of shifting centers to semi-boundary vertices could lead to some result. 
+\end{itemize}
+\subsection{Independent Trial}
 \begin{itemize}
@@
 
-But we still might have too few centers in dense cliques while just sufficient in other parts or maybe even having residual capacities in sparse areas.
+But we still might have too few centers in dense areas while just sufficient in other parts or maybe even having residual capacities in sparse areas.
 We also have a counter example for the same as shown in the figure below.
 The centers are represented by the rectangular marks on the vertices.
-The left most center is covering many clients within a distance of <=2 where as the same cannot be said for the other centers.\\
+The left most center is covering many clients within a distance of <=2 whereas the situation is the other extreme for the other centers.\\
 \begin{figure}[H]
@@
 \begin{center}
-\includegraphics[scale=0.25]{d2.jpg}
+\includegraphics[scale=0.5]{d2.jpg}
   \caption{Clique formation}
@@
 Following this we have free centers available which we can place in dense cliques with high degree of vertices.
-Like in the figure below in the nodes that were centers in $G^2$ are represented by square labels in the left figure and diamond label on the right while the one which we replace them by in $G^4$ is represent by the square in the right figure.
+Like in the figure below, centers in $G^2$ are represented by square labels in the left figure and diamond label on the right while the one that replaces them in $G^4$ is represented by a square in the right figure.
 \begin{figure}[H]
@@
 \end{figure}
-Like here we obtain one extra center. The problem still remains on how to keep obtaining such centers other than by merging and then placing them at an appropriate position.
+Why are we doing this?
+By doing the above $merging$ operation, we obtain one extra center that can be placed at any location of our choice.
+The problem still remains on how to keep obtaining such centers other than by merging and then placing them at an appropriate position.
 
-Further, we try to come up with some kind of data structure that might help us make some claims on the lower bound on K. \begin{figure}
-
+Further, we tried to come up with some kind of data structure that might help us make some claims on the lower bound on K, when the edge reassignment operation stops at a local optima.
+\begin{figure}[H]
+\includegraphics[scale=0.4]{diag8.jpg}
+\caption{Level Structure}
 \end{figure}
-As above we make a level structure with the cliques in set $C_l$ as taken before at level l.After a reassignment is performed, the structure changes, because, always the cliques are taken to be a center and its neighbors.
-After a reassignment, the set of neighbors of (more than or equal to 2) centers change, and also, their capacities change, thus moving them to different levels than present.
+As shown above, we make a level structure with the set domains with center $C_i$ by placing the domains of size $l$ at level $l$.
+This is the final structure after all reassignments which follows the upcoming theorems.
+Also edges $A, B and C$ cannot be present.\\ We say it is the final structure because, after a reassignment operation, the set of neighbors of (more than or equal to 2) centers change, and also, their capacities change, thus moving them to different levels throughout the edge reassignment phase.
 \\\\\textbf{Theorem:}
-When there can be no more edge reassignments, then no center at level l, has an edge of length <= 4 to any node in level l’ >= l+2 for all l. 
+When there can be no more edge reassignments, then no center at level $l$ is within a distance $\leq 4$ to any node in level $l’ \geq l+2$ for all $l$. 
 \\\\
-\textbf{Proof:}
-After there can be no more reassignments, let there exists such a center C at a level l which has an edge to some node P belonging to some level l’ >= l + 2.
-Let C’ be the center covering the node P.
-Then we can do a reassignment step such that P gets assigned to C instead of C` thereby moving C` one level down and C one level up.
+\textbf{Proof:}This case is depicted in by edge $A$ in the level structure.
+After there can be no more reassignments, let there exists such a center $C$ at a level $l$ which has an edge to some node P belonging to some level $l’ \geq l + 2$ i.e.
+let edge A exist.
+Let $C’$ be the center covering the node $P$.
+Then we can do a reassignment step such that $P$ gets assigned to $C$ instead of $C`$ thereby moving $C`$ one level down and $C$ one level up.
 Thus the max degree can decrease this way removing one clique at a time.
 
-\begin{figure}
+This contradicts our assumption that no more reassignment is possible.\\\\
+\textbf{Theorem:} When there can be no more reassignments, if a center $C_l$ at level $l$ is within distance $\leq$ 4 to a non-center at level $l+1$, then any center $C'< l$ at levels $< l$, will not be within a distance $\leq$4 from any node in the domain of $C_l$.\\\\
+\textbf{Proof:}
+This situation is represented by edge $B$ in the level structure.
+We will prove by contradiction.
+Let us say such a case exists, i.e., edge $B$ in the figure exists.
+Then, we can do a series of reassignments, to reduce the degree of a center at $C_l$ at some level $\geq l + 1$.
+This is a contradiction, since we assumed in the beginning that we have reached atleast a local optima and there can be no more reassignments.
 
+\end{itemize}
+\begin{appendices}
+\section{The Integer Program}
+\begin{center}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{1.png}
+  \caption{Sample Code:Integer Program-1}
+  \label{Figure 2}
 \end{figure}
 
-This contradicts our assumption that no more reassignment is possible.
+\begin{figure}[H]
+ \includegraphics[scale=1.25]{2_1.png}
+  \caption{Sample Code:Integer Program-2}
+  \label{Figure 3}
+\end{figure}
 
-\end{itemize}
-\subsection{Counter Examples}
-\subsection{Current Scenario}
+\end{center}
+\section{Local Search Program}
+\begin{flushleft}
+\begin{figure}[H]
+ \includegraphics[scale=1]{a.png}
+  \caption{Code}
+  \label{Figure 4}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[scale=1.25]{b.png}
+  \caption{Code}
+  \label{Figure 5}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[width=18cm,height=18cm]{c.png}
+  \caption{Code}
+  \label{Figure 6}
+\end{figure}
+
+\end{flushleft}
+\section{Random Graph Generation}
+\begin{figure}[H]
+ \includegraphics[scale=1]{prajwal.png}
+  \caption{ }
+  \label{Figure 7}
+\end{figure}
+\section{Star Graph Generation}
+\begin{figure}[H]
+ \includegraphics[scale=1]{g1.png}
+  \caption{Code}
+  \label{Figure 8}
+\end{figure}
+
+\begin{figure}[H]
+ \includegraphics[scale=1]{g2.png}
+  \caption{Code}
+  \label{Figure 9}
+\end{figure}
+\section{Unit Square Graph Generation}
+
+\end{appendices}
+
 \end{document}

### 2016-07-07 LocalSearchAlgorithm/ls.py
Hopefully final cleaning of code and commit

@@ -4,7 +4,7 @@ from random import shuffle, randint
 from collections import defaultdict
 import matplotlib.pyplot as plt
 import pprint, pickle
-from ls_random import main as randomizedLS
+from ls_randomized import main as randomizedLS
 
 #Generating a random graph using snap
 def randomGraph(n,edges):
@@ -94,11 +94,10 @@ def doOneSwaps(G, S, L):
 	while nx.maximum_flow_value(getFlowGraph(G, Vmax, L), 's', 't') > nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't'):
 		S = Vmax
 		Vmax = getVmax(G, S[:], L)
-	#print nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't')
 	return S
 
 def main(N,adj,k,L):
-	iterations = 10
+	iterations = 5
 	result = 'Failed'
 	while iterations > 0 and result == 'Failed':
 		print iterations
@@ -109,6 +108,7 @@ def main(N,adj,k,L):
 		result = None
 		#max flow value cannot be greater than the number of nodes in the graph or set V
 		if nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't') == N:
+			# uncomment this to get assignments
 			'''_,flows = nx.maximum_flow(getFlowGraph(G, S, L), 's', 't')
 			edges = set(G.edges())
 		        #if a flow exists along a particular path assigning v to that vertex in S
@@ -131,9 +131,14 @@ def main(N,adj,k,L):
 		else:
 			result = 'Failed'
 		iterations -= 1
+
 	if result == 'Failed':
+		''' Do randomization if the max-cover approach fails'''
 		result = randomizedLS(N, adj, k, L)
-	'''if result == 'Failed' and N <= 30:
+
+	if result == 'Failed':
+		''' Save the graph as an image, and its adjacency matrix
+			as a pickle file '''
 		pos = nx.spring_layout(G)
 		nx.draw_networkx_nodes(G, pos, nodelist=S, node_color='b', node_size=200)
 		nx.draw_networkx_nodes(G, pos, nodelist=list(set(G.nodes()) - set(S)), node_color='r', node_size=200)
@@ -143,5 +148,6 @@ def main(N,adj,k,L):
 		a = [[0 for _ in xrange(N)] for _ in xrange(N)]
 		for key, val in adj.iteritems():
 			a[key[0]][key[1]] = val
[…]

### 2016-07-07 LocalSearchAlgorithm/ls_randomized.py

@@ -94,7 +94,6 @@ def doOneSwaps(G, S, L):
 	while nx.maximum_flow_value(getFlowGraph(G, Vmax, L), 's', 't') > nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't'):
 		S = Vmax
 		Vmax = getVmax(G, S[:], L)
-	#print nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't')
 	return S
 
 def main(N,adj,k,L):
@@ -109,6 +108,7 @@ def main(N,adj,k,L):
 		result = None
 		#max flow value cannot be greater than the number of nodes in the graph or set V
 		if nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't') == N:
+			#uncomment the below to compute assignments
 			'''_,flows = nx.maximum_flow(getFlowGraph(G, S, L), 's', 't')
 			edges = set(G.edges())
 		        #if a flow exists along a particular path assigning v to that vertex in S
@@ -131,7 +131,9 @@ def main(N,adj,k,L):
 		else:
 			result = 'Failed'
 		iterations -= 1
-	'''if result == 'Failed' and N <= 50:
+	if result == 'Failed':
+		''' Save the graph as an image, and its adjacency matrix
+			as a pickle file '''
 		pos = nx.spring_layout(G,k=0.5)
 		nx.draw_networkx_nodes(G, pos, nodelist=S, node_color='b', node_size=200)
 		nx.draw_networkx_nodes(G, pos, nodelist=list(set(G.nodes()) - set(S)), node_color='r', node_size=200)
@@ -141,5 +143,5 @@ def main(N,adj,k,L):
 		a = [[0 for _ in xrange(N)] for _ in xrange(N)]
 		for key, val in adj.iteritems():
 			a[key[0]][key[1]] = val
-		pickle.dump(a,open('failures/' + fname,'w'))'''
+		pickle.dump(a,open('failures/' + fname,'w'))
 	return result

### 2016-07-07 main.py

@@ -8,7 +8,7 @@ import networkx as nx
 import matplotlib.pyplot as plt
 
 def randomGraph(n):
-	edges=input("No. of edges:")
+	edges=2*n
 	UGraph = snap.GenRndGnm(snap.PUNGraph, n, edges)
 	adj = dict()
 	for x in range(n):
@@ -22,9 +22,11 @@ def randomGraph(n):
 	return adj
 
 def integerProgram(N,adj=None,p=None,W=None):
-	# adj = randomGraph(N)
-	if not adj: 
+	if adj == 'unit': 
 		adj = UnitSquareGraph(N,p,W).adj
+	elif adj == 'random':
+		adj = randomGraph(N)
+
 	edges = (sum([val for key, val in adj.iteritems()]) - N)/2
 	L = N/10
 
@@ -66,16 +68,20 @@ def integerProgram(N,adj=None,p=None,W=None):
 
 	# solve the problem using GLPK
 	status = prob.solve(GLPK(msg=0))
-	list_var=prob.variables()
-	list_cen=list_var[(len(list_var)-N):]
-	count=0
+	list_var = prob.variables()
+	list_cen = list_var[(len(list_var)-N):]
+	count = 0
 	for v in list_cen:
-	    if(v.varValue==1.0):
-	    	count+= 1
+	    if(v.varValue == 1.0):
+	    	count += 1
 	result = '{}\t{}\t{}\t{}'.format(N,edges, LpStatus[prob.status], count)
 	return result, adj
 
 def test_counter_cases():
+	'''
+		Execute the optimal and Local search for
+		countercase graphs saved in the failures/test/ folder.
+	'''
 	header = '\t'.join(['Nodes','Edges','Status','K','Local Search'])
 	print header
 	res = []
@@ -97,14 +103,30 @@ def test_counter_cases():
 		pass
 	with open('results','w') as f:
 		f.write('\n'.join(res))
-	
-def main():
+
+def randomTester():
+	'''
+		Test random graphs
+	'''
+	print '\t'.join(['Nodes','Edges','Status','K','Local Search'])
+	NODE_LIMIT = 80
+	N = randint(20, NODE_LIMIT)
+	opt, adj = integerProgram(N,'random')
+	ls = localSearch(N,adj,int(opt.split('\t')[-1]),N/10)
+	result = '\t'.join([opt, ls])
+	print result
+	return result
[…]

### 2016-07-07 starGraphGen.py

@@ -12,12 +12,6 @@ class Graph(object):
 			self.N = self.k*self.l
 			self.p = specs.p	# supplementary edge probability
 			self.starGraph()
-
-		elif specs.struct == 'random':
-			self.N = specs.N 
-			self.edges = specs.M
-			self.randomGraph()
-
 		else:
 			raise ValueError('Invalid specifications!')
 
@@ -30,14 +24,6 @@ class Graph(object):
 				self.adj[(x,y)] = 0
 		for i in xrange(self.N):
 			self.adj[(i,i)] = 1
-
-	def randomGraph(self):
-		UGraph = snap.GenRndGnm(snap.PUNGraph, self.N, self.edges)
-		self.initAdj()
-
-		for EI in UGraph.Edges():
-			self.adj[(EI.GetSrcNId(),EI.GetDstNId())] = 1
-			self.adj[(EI.GetDstNId(), EI.GetSrcNId())] = 1
 
 	def starGraph(self):
 		self.initAdj()

### 2016-07-08 LocalSearchAlgorithm/ls.py
Update ls.py

@@ -40,7 +40,8 @@ def getS(G,k):
 	shuffle(nodes)
 	return nodes[:k]
 
-#making FG a directed flowgraph to give as input to max flow functions ( s-->V-->S-->t )
+#making FG a directed flowgraph to give as input to max flow functions
+#( s-->V-->S-->t )
 def getFlowGraph(G, S, L):
 	FG = nx.DiGraph()
 	N = len(G.nodes())
@@ -91,7 +92,8 @@ def getVmax(G, S, L):
 #changing S and Vmax by one swaps so as to achieve the max flow possible after each obtained S
 def doOneSwaps(G, S, L):
 	Vmax = getVmax(G, S[:], L)
-	while nx.maximum_flow_value(getFlowGraph(G, Vmax, L), 's', 't') > nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't'):
+	while nx.maximum_flow_value(getFlowGraph(G, Vmax, L), 's', 't') >
+	      nx.maximum_flow_value(getFlowGraph(G, S, L), 's', 't'):
 		S = Vmax
 		Vmax = getVmax(G, S[:], L)
 	return S

### 2016-07-08 unitSquare.py
Update unitSquare.py

@@ -7,12 +7,10 @@ class UnitSquareGraph(object):
 		self.P = P
 		self.W = W
 		points = [[random(),random()] for _ in xrange(self.N)]
-		self.dist = [[None for _ in xrange(self.N)] for _ in xrange(self.N)]
-
+		self.dist = [[None for _ in xrange(self.N)] for _ in xrange(self.N)
 		for i in xrange(self.N):
 			for j in xrange(self.N):
 				self.dist[i][j] = self.dist[j][i] = self.lpNorm(points[i], points[j], self.P)
-
 		self.adj = self.getAdj()
 		self.nxGraph = self.NXify()
 

### 2016-07-08 unitSquare.py
Fixing bug created by Anya

@@ -7,7 +7,7 @@ class UnitSquareGraph(object):
 		self.P = P
 		self.W = W
 		points = [[random(),random()] for _ in xrange(self.N)]
-		self.dist = [[None for _ in xrange(self.N)] for _ in xrange(self.N)
+		self.dist = [[None for _ in xrange(self.N)] for _ in xrange(self.N)]
 		for i in xrange(self.N):
 			for j in xrange(self.N):
 				self.dist[i][j] = self.dist[j][i] = self.lpNorm(points[i], points[j], self.P)

### 2016-07-10 Capacitated K-Centre.tex
Add files via upload

\documentclass[12pt,a4paper,onecolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{mathpazo}
\usepackage{float}

\usepackage{color}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=red,
    linktoc=all
}
\usepackage[toc,page]{appendix}

\addtocontents{toc}{\protect\hypertarget{toc}{}}
\usepackage{algorithmic}
\usepackage{newunicodechar}
\newunicodechar{ﬁ}{fi}
\newunicodechar{ﬂ}{fl}

\author{Anya Chaturvedi \\ Sagar Sahni \and K. R. Prajwal \\ Ketaki Vaidya  }
\title{%
  The Capacitated K-Centre Problem\\
  \large Summer Internship Report 
  }
 \date{}
\begin{document}
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\center

%\textsc{\LARGE Capacitated K-Centre Problem}\\[1.5cm] % Name of your university/college
% Minor heading such as course title

\HRule \\[0.4cm]
{ \huge \bfseries Capacitated K-Centre Problem}\\[0.4cm] % Title of your document
\HRule \\[1cm]
 \textsc{\Large Summer Internship Report}\\[1cm] % Major heading such as course name
{\large May $9^{th}$ - July $11^{th}$, 2016}\\[0.5cm]
%----------------------------------------------------------------------------------------
%   AUTHOR SECTION
%----------------------------------------------------------------------------------------

\includegraphics[scale=0.06]{iitd_logo.png}\\[0.5cm] % Include a department/university logo - this will require the graphicx package
\textsc{\large Indian Institute of Technology, Delhi}\\[9cm]

 % Date, change the \today to a set date if you want to be precise

%----------------------------------------------------------------------------------------
%   LOGO SECTION
%----------------------------------------------------------------------------------------

 \begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{\\Authors:}\\
Anya Chaturvedi\\
K.R. Prajwal\\
Sagar Sahni\\
Ketaki Vaidya
 % Your name
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Dr. Naveen Garg \\
Professor\\
Dept. of CSE\\
IIT Delhi % Supervisor's Name
\end{flushright}
\end{minipage}\\[2cm]
%----------------------------------------------------------------------------------------

\vfill % Fill the rest of the page with whitespace

%\section[Abstract]{Abstract \begin{flushright}\hyperlink{toc}{TOC}\end{flushright}}
\newpage
\thispagestyle{empty}

\begin{center}

\large{Department of Computer Science and Engineering}\\[0.5cm]
\normalsize
\textsc{Indian Institute of Technology Delhi}\\[2.0cm]

\LARGE Certificate\\[1 cm]

\end{center}
\normalsize \begin{flushleft}
This is to certify that the students whose names are given below have done their summer internship on \textbf{The Capacitated K-Centre Problem} under my guidance \\for a duration of two months  in Summer - 2016  and have submitted this report.
\end{flushleft}
\vspace{0.5cm}
\begin{table}[h]
\centering
\begin{tabular}{lr}
 Name & Institute \\
\\
Anya Chaturvedi & Motilal Nehru National Institute of Technology, Allahabad \\ 
K.R. Prajwal &  National Institute of Technology, Tiruchirappalli \\
Sagar Sahni & SRM University, Kattankulathur \\
Ketaki Vaidya & National Institute of Technology, Silchar
\end{tabular}
\end{table}

\vspace{4cm}

 \begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{\\Date:}\\

\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright}

\large Dr. Naveen Garg \\
(Supervisor)% Supervisor's Name
\end{flushright}
\end{minipage}\\[2cm]

\newpage
\thispagestyle{empty}

\begin{center}

\LARGE ACKNOWLEDGEMENTS\\[2 cm]

\end{center}
\large \begin{flushleft}
We wish to express our sincere gratitude to Professor Naveen Garg for letting us be a part of his research group for the summer.\end{flushleft}
\begin{flushleft}We also wish to thank the research scholars, Jatin, Aounon and Nikhil for their continuous  help and guidance in carrying out our implementations and giving us topics to brainstorm upon.\end{flushleft} \begin{flushleft}Thank you to all the above mentioned for taking out time for us and providing us with an enriching and memorable experience.\end{flushleft} \begin{flushleft}

 - Anya, Prajwal, Sagar \& Ketaki.
\end{flushleft}

\end{titlepage}

\tableofcontents

\section{Abstract}
The capacitated $K$-centre problem is basically a facility location problem, where one is asked to assign $K$ points to $K$ facilities in a given distance metric. In doing this we minimise
the maximum distance from a vertex to the facility to which it is assigned while keeping in mind that each facility may be assigned at most $L$ vertices including itself. This problem is known to be NP-hard.

We show our attempts at solving this problem, counterexamples that we studied and a few basic implementations of the same. Starting with a more formal description of our problem, we describe the flow method which helps us verify a solution to the problem. Next, we show how we implemented the integer program and a partially correct local search algorithm. In implementing the above programs we have used three ways for making the input graphs. One is a random graph, second a more clustered form i.e. a star graph, and the last one is generated by taking points in a unit square. Other than this we have included a few observations which may not be very conclusive but are our attempts to solve the problem over the summer.
\section{A Look at the Problem}
The problem studied by us is actually a generalization of the $K$-centre problem which we explain here. 
\subsection{The $K$-Centre Problem}
Given $n$ vertices with specified distances, one wants to build $K$ facilities at different vertices such that each vertex has access to a facility and minimise the maximum distance between each vertex and the corresponding facility. This problem is NP-hard. An approximation algorithm with a factor of $\eta$, for a minimization problem, is a polynomial time algorithm that guarantees a solution with cost at most $\eta$ times the cost of an optimal solution. For the basic $K$-centre, methods have been presented for obtaining an approximation factor of 2. Given a complete undirected graph $G$ = $(V, E)$ with distances $d(v_i, v_j) \in \mathbb{N}$ satisfying the triangle inequality, we have to find a subset $S \subseteq V$ such that $|S| = k$ and such that it covers all $V$.\\\\
 \textbf{Input:}\\1. A metric space, or, in other words, a complete graph that satisfies the triangle inequality.\\2. An upper bound on the number of centres, $K$.\\\\
\textbf{Output:}\\
$$\min_{S \subseteq V}\max_{v \in V}\min_{s \in S}d(v,s)$$
where $d$ is the distance function.

This is quite similar to the problem of placing $K$ disks such that all points are covered in the set $V$ and the maximum radius required to do so is minimised.

\subsection{The Capacitated K-Centre}
The capacitated $K$-centre problem is nothing but a generalization of the $K$-centre problem. We have to
output a set of at most $K$ centres, as well as an assignment of vertices to centres. No more than $L$ vertices may be assigned to a single centre. Under these constraints, we
wish to minimise the maximum distance between a vertex $u$ and its assigned centre
$\varphi (u)$. \\\\
\textbf{Input:}\\1. A metric space, or, in other words, a complete graph that satisfies the triangle inequality.\\2. An
upper bound on the number of centres, $K$.\\3. A maximum capacity for each centre, $L$.\\\\
\textbf{Output:}\\
$$ \min_{S \subseteq V}\max_{u \in V}d(u,\varphi(u)) $$such that,   $$|\{u|\varphi(u) = v\}|\leq L \forall v \in S,$$\\where,   $$\varphi : V \rightarrow S.$$\\
The first constant factor polynomial time approximation
algorithm for this problem was with an approximation factor of 10. Later, a 6-approximation was found which is the best up till date while a 5-approximation works when we can assign multiple centres at any single vertex without counting the center itself while calculating the capacity used.

Initially we went through the sections 2.6 and 9.3 of Williamson \& Shmoys which solve the problem of finding the minimum degree spanning tree problem which is also NP-hard. Here we learnt of methods like local search used to create approximation algorithms. Next we read a few papers related to our problem and gathered what is presented in the upcoming sections.
\section{Checking the Feasibility of the Input Graph}
We say that if we solve the capacitated $K$-centre problem then it will be equivalent to getting the minimum value of $W$ for which $G(W$) has a capacitated dominating set of size $K$, where $G(W)$ refers to the graph having all edges with edge weight less than or equal to $W$.

We can easily set up such an equivalence if we slightly modify our problem. Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$ we say that $S \subseteq V$ is a capacitated dominating set if there exists a mapping $f : V \rightarrow S$ (domination mapping) such that:\begin{enumerate}

\item $\forall v \in V ,\:\forall s \in S,\:f(v) = s \Longrightarrow (v,s) \in E$\\ \item $\forall s \in S,\:| \{ v \in V| f(v) = s \} | \leq c(s)$
\end{enumerate}In the new version of the $K$-centre problem, the goal is to get a set $S$ of $K$ vertices and an assignment $h : V \rightarrow S$ of every vertex (in $V$) to an open centre such that the greatest distance between a vertex and the centre it is assigned to is minimised and no facility is assigned more vertices than its capacity. Note that the assignment is not for all vertices in $V$. We make the assumption that every centre serves itself and the capacity $(L(v))$ of a vertex $v \in V$ is the maximum number of clients it can serve (excluding itself).

Now we can say that solving the capacitated $K$-centre problem is equivalent to getting the minimum value of $W$ for which $G(W)$ has a capacitated dominating set of size $K$. 
$S \subseteq V$ is an optimal solution to the capacitated $K$-centre problem if and only if $w(S)$ is the minimum value of $W$ for which the graph $G(W)$ has a capacitated dominating set of size $K$.
It is also easy to verify that a capacitated dominating set of size $K$ in $G(w(S))^i$, for some $i$ and some optimal solution $S$, forms an $i$-approximation for the $K$-centre problem.

However, note that the capacitated dominating set problem is an NP-complete problem. Therefore, we cannot get a capacitated dominating set of size $K$ in polynomial time, unless $P = NP$. Similar to the uncapacitated version, the capacitated version too is hard to approximate within a factor of 2.
\subsection{Verification using a Network Flow }
Given a graph $G = (V,E)$ and a capacity function $c : V \rightarrow N$, checking whether $S \in V$ is a capacitated dominating set can be viewed as a network problem. We construct a directed graph $G_S = (V_S,E_S)$ as follows:\begin{enumerate} 
\item $V_S = V \cup \{s,t\}$
\item $E_S = \{(s,v_i) | v_i \in V \} \cup \{(s_i,t) | s_i \in S \}\cup \{(v_i,s_i) | v_i \in V \wedge s_i \in S \wedge (v_i,s_i) \in E \}$\end{enumerate} Let $c_S : E_S \rightarrow N\mathbb{N}$ be the capacity function such that, $$c_S(e_{uv}) =\left\{ \begin{array}{cc}c(u),  &  v = t \\\\ 1, & otherwise \end{array}\right.$$
As defined above, in the final graph $G_S$ we add two more vertices s (source) and t (sink) to the vertex set of G. We add directed edges from s to all vertices in $V$, from each vertex in $V$ to its neighbours in $S$ and each vertex in $S$ to $t$. We take the capacity function to be equal to the capacity of the source vertex for edges incident on $t$ and to be equal to 1 for every other edge in $E_S$. \\
The flow network as described has been shown in Figure 1.
\begin{flushleft}
 \begin{figure}[H]
 \begin{center}
 \includegraphics[scale=0.5]{diag2.jpg}
 \end{center}
  \caption{The flow network}
  \label{Figure 1}
\end{figure}
\end{flushleft}
  Now it is easy to verify that, S is a capacitated dominating set in G if and only if $G_S$ has a maximum coverage of $|V|$ from $s$ to $t$ equal to the total vertices in the graph.

\section{The Integer Program}
Linear programming is a mathematical technique for maximising or minimising a linear function of several variables such as output or cost. The decision variables with respect to which the optimum is obtained can come out to be fractional or integral. An integer programming problem is a mathematical optimization or feasibility program in which
some or all of the variables are restricted to be integers which makes it a subset of linear programming. Ours is a problem where we
wish to minimise the maximum distance between a vertex u and its assigned centre thus our integer program is framed as:
\\

\textbf{Objective Function:}\\
\hspace{15mm} $$z=\sum_{i=1}^{N}cen[i]$$
\\
\textbf{Variables:}\begin{enumerate}
\item \textit{\textbf{cen}} - an integer dictionary which specifies the centres among the vertices
where if $cen[i]=1$ then the $i^{th}$ index vertex is taken to be a centre otherwise not.\item \textit{\textbf{assignments}} - a dictionary, $assignments[i][j]=1$ will represent that the $j^th$ index vertex is assigned to the centre created at the $i^th$ index vertex, we initialise it with the adjacency matrix
\item \textit{\textbf{$N$}} - the total number of vertices
\item \textit{\textbf{$adj$}} - a dictionary which stores the adjacency matrix of the graph 
\end{enumerate}
\textbf{Constraints:}
\begin{enumerate}
\item $\forall i \sum_{j=1}^{N}assignments[i][j]\leq L*cen[i]$\\\hspace{1cm}\ldots makes sure no more than $L$ vertices are assigned to a centre
\item $\forall j \sum_{i=1}^{N}assignments[i][j] = 1$\\\hspace{1cm}\ldots a vertex can be assigned only to a single centre
\item $\forall i \, \forall j \, assignments[i][j] \leq cen[i]$\\\hspace{1cm}\ldots a vertex can only be assigned to a vertex if the later is a centre
\item $\forall i , \forall j \, assignments[i][j] \leq adj[i][j]$\\\hspace{1cm}\ldots 
assignment of vertices can only be done if the edge between a vertex and its corresponding centre is present in the original graph

\end{enumerate}

You can refer to the code in Appendix A.

\section{Local Search Algorithm}
Local search can be used on problems that can be formulated as finding a solution by maximising a criterion among a number of candidate solutions.
A local search algorithm starts from a candidate solution and then iteratively moves to a neighbour solution. We move from solution to solution in the space of candidate solutions (the search space) by applying local changes, until a solution optimal is found.
We have used a local search algorithm which was formed by Aounon which is actually a randomised algorithm. It does not work on a set of graphs but by increasing the number of iterations on the same graph it gradually gives the solution for most as the probability involved increases.

Here, we start with a set $S$ of random $K$ vertices in graph $G$ . Let $S$ be the set of all $K$ vertex sets which are formed by replacing one vertex in $S$ by a vertex in $V$ (one-swap vertex sets). We look for the set in $S$ which maximises the number of dominated vertices. If one of the set dominates more vertices than current $S$ then we set $S$ to that set and continue the process till we have reached a local optima. We do the assignments through a network flow graph.\\\\\\
\textbf{Algorithm:}
\begin{algorithmic}[1]
\STATE $S \leftarrow {v1, v2,…., vk}$
\STATE $S' \leftarrow {one-swap\: vertex\: sets\: of\: S}$
\WHILE {$MaxFlow(G_{V_{max}}, c_{V_{max}}) > MaxFlow(G_S,c_S)$}
\STATE $S \leftarrow V_{max}$
\STATE $S' \leftarrow {one-swap\: vertex\: sets \: of\: S}$
\STATE $V_{max} \leftarrow argmax _{V \in S} MaxFlow(G_V , c_V )$
\ENDWHILE 
\IF{$MaxFlow(G_S , c_S) = n - k$}
\FORALL {$v \in V$}
\IF{$f_{max}(v,s)=1$}
\STATE $h(v) = s$
\ENDIF
\ENDFOR
\RETURN $S, h$
\ENDIF
\end{algorithmic}

You can refer to the code in Appendix B.

\section{Graph Generation}
\subsection{Random Graph}
For testing the implemented algorithms on random graphs, SNAP, a Python based system developed by Stanford University was used. It takes the number of nodes and edges as input and gives a random sub graph of a data set which we convert represents to an adjacency matrix, ready to be fed into the Integer Program and local search algorithm.

You can refer to the code in Appendix C.

\subsection{Star Graph}
In an attempt to try our programs on a more clustered data set, this program was implemented to create sparsely-connected star graphs, with edges chosen to be added with a probability p.

We were able to get 100\% accuracy and this was the strongest dataset we tested upon.

You can refer to the code in Appendix D.

\subsection{Unit Square}
On discussing our above mentioned methods with Sir he suggested another way for making the input graphs which he felt might give us better  results for further analysis. 
The method proceeds by taking $N$ random points in a unit square.
The edge weight between all possible pairs of these $N$ points are calculated by using different $L^p$ norms, for $p \geq 1$.
$W$ is chosen which denotes the maximum edge weight allowed in a particular thus reducing the number of edges in the otherwise obtained complete graph. 
The graph is built with the $N$ random points as nodes and edges $(a,b)$ if distance between $(a,b)$ is $\leq W$, for all $a,b$ $\in$ $N$. 
This graph is used to obtain the optimal $K$ using a capacity, which we have taken as $L = N/10$.

We have used the same graph to check if the randomised local search algorithm yields the optimal solution with the above obtained $K$ and $L$.

Even though this did not strike at first on why this will be in any manner be different than using random graphs, still we decided to proceed with the implementation. During our visualization of the graphs created, we saw that this method gave us a very large variety of graphs, in the sense that the graphs had local clusters, articulation points, isolated vertices, cliques and a wide variation in the degrees of the nodes.

We checked it on the integer program, local search and randomised local search programs. Mostly it worked but took a long time as we have iterate the local search for 5-10 iterations to increase the chance of it being successful. If somehow the complexity can be reduced we can see how well it works for larger graphs. The complexity as of now is the order of O($n^7$). At present it is working very well for below 40 nodes giving almost a 100\% accuracy but after we clocked it up to 80 nodes(we could not increase more) we found that the accuracy drops sharply to 98-99\%  i.e. one or two failures for every 110 nodes. Though it gives failure few times it is difficult to analyse due to the large number of vertices in the failed examples.

 Further, we came up with minor hacks and tweaks to get the best of randomization and non-randomization in our algorithm by including them in a single run and could get all correct on several test sets of 110 unit square graphs each. However, this still exists as a minor tweak, and we are not able to analyse pictorially for larger graphs such as 80 nodes as we did for $\leq 40$ nodes. We hence, tried a different approach of representing it as a bipartite graph, but that was not possible through the networkx library which we have used. We hence would need a better method to analyse large graphs of 80 nodes or more.

You can refer to the code in Appendix E.
\section{Observations made}
This section is a collection of all our trials and errors during our exploration of this topic along with few of the concepts learnt which provide the base for these trials.
\subsection{Lower Bound on K}
Let us say we make disjoint set of partitions of our input graph nodes such that each partition has two types of vertices, inner and boundary. The inner vertices are the ones which have no edges with vertices outside their partition, while the boundary vertices are the ones which do have edges to other partitions. Let the $i^{th}$ partition be represented by its inner vertices $C_i$ and its boundary vertices as $B(C_i)$.

Since we know K vertices can cover up to L vertices so the maximum vertices that can be covered is $V = K*L$. Hence the minimum $K$ required to cover $V$ vertices is $\lceil V/L\rceil$. This is a naive lower bound on $K$. But using this concept, we may get a better lower bound.

Here, in the partitioning as described above, for the vertices other than the boundary vertices we can say that they can only be covered by vertices of their own partition thus we need to open centres in the partition itself for such vertices. If we say there are $p$ partitions then $\sum_{i=1}^{p}\lceil (C_i-B(C_i))/L\rceil$ vertices are required at least to cover the graph and hence this comes to be a lower bound. \\The above bound has been presented in a research paper already. We observed that, the above mentioned paper is not involving the boundary vertices in formulating a lower bound. So, we toyed for some time with ideas on involving the boundary vertices. We thought using the residual capacity, i.e. $\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$ we may be able to cover some or even all of the boundary vertices. Through this we can decide opening more centres or shifting the centres so as to cover more boundary vertices. But all of this depends upon the connectivity of the particular graph and what kind of partition we take which did not look promising after a point of time either.\\ Later when Jatin and Aounon started thinking towards this way we again applied our thinking on the same.

Let us say we partition the graph into sets of nodes $C_i - B(C_i) \: 1 \leq i \leq N$ with the boundary vertices outside the partitions as shown in Figure 2.

\begin{flushright}
\begin{figure}[H]
\includegraphics[scale=0.2]{diag7.jpg}
\caption{Partitioning the Vertex Set}
\end{figure}
\end{flushright}

As discussed before, the minimum number of centres we need to place inside the partition $C_i$ is $\lceil ((C_i-B(C_i))/L) \rceil$. The residual capacity, which can cover boundary vertices as mentioned above is, $\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$ and can be used to cover the boundary vertices. To implement this, a flow network is created as labelled in Figure 3.

\begin{center}
\begin{figure}[H]
\includegraphics[scale=0.5]{diag1.jpg}
\caption{$Z=\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$}
\end{figure}
\end{center}
Here $Z$ refers to the remaining capacity of the centres as opened in the inner vertices i.e $\lceil (C_i-B(C_i))/L\rceil*L-(C_i-B(C_i))$.
Now there are two cases:
\begin{itemize}
\item If we are not able to find a flow to cover all the boundary vertices within a distance of 2 with the residual capacities, then there exist a set of partitions $P_1, P_2,\ldots P_i$ and $B(P_1), B(P_2),\ldots B(P_i)$ for which Hall’s theorem does not hold i.e.: 
 $$|B|> {\sum_{i=1}^{N}\lceil (P_i-B(P_i))/L\rceil*L-(P_i-B(P_i))}$$
which after rearrangement becomes:\\
$$\lceil (\sum_{i=1}^{N}P_i)/L \rceil > \sum_{i=1}^{N} \lceil P_i/L \rceil   $$
This, in turn, means we can merge the above set of partitions to get a better lower bound. The boundary vertices will always be in the interior of the new set of partitions, because if they were not then it can be covered by a residual capacity, a contradiction.

\item If the flow exists, this is where we are stuck again. We do not know if there is such a set of centres we can choose such that we can make use of all the necessary residual capacity which is actually taken into account by the flow network. 
Our attempt to resolve this:

\begin{flushleft}
\begin{figure}[H]
\includegraphics[scale=0.55]{anya.jpg}

  \caption{Reassignment of Centres}
\end{figure}
\end{flushleft}

We define ( the nodes labelled in Figure 4) as:
\begin{itemize}

\item Node type: $a$ : A centre in a partition which does not have edge to any boundary vertex.
\item Node type: $q$ : An interior non - centre, which is a client of $a$ and adjacent to a boundary vertex. We will call it the semi boundary vertex. 
\end{itemize} 
We observe that if we make as many semi-boundary centres as possible, such that they cover maximum number of boundary vertices, by shifting the centres located at $a$ to $q$ then we can come to a conclusion. 
If we make the semi-boundary vertex $q$ as a centre, then it will cover all the clients that have been covered by its respective centre $a$, but now the minimum maximum distance would be at most 4*OPT. Also, we would need to shift to such a set of semi-boundary vertices that maximises the number of distinct boundary vertices getting covered. So, we make a flow network for the same as shown in Figure 5.

\begin{flushleft}
\begin{figure}[H]
\includegraphics[scale=0.5]{diag3(2).jpg}
\caption{Flow to exchange Semi-boundary vertices with Existing Centres}
\end{figure}
\end{flushleft}
But we cannot make greedy moves and just move to the semi-boundary vertices with maximum boundary neighbours, as it is very necessary to make sure these boundary neighbours are distinct. To ensure this, we have Figure 6.
\begin{center}
\begin{figure}[H]
\includegraphics[scale=0.35]{diag4.jpg}
\caption{New Flow Method}
\end{figure}\end{center}
We keep the capacity of all edges in this flow network as 1 but modify the edge weights of edge weights between $B$, $Q$ and $A$ to keep a check. Between $A$ and $Q$, $e_1$ the remaining capacity of $q_i$ which is -- $L-$the number of non centres transferred to it through $a_i$ is taken as the edge weight between $q_i$ and $a_i$. While the edge weight between $B$ and $Q$, $e_2$ is equal to the inverse of the number of boundary vertices that the corresponding $q$ will cover if selected. 
\begin{center}
\begin{figure}[H]
\includegraphics[scale=0.3]{diag6.jpg}
\caption{Case of 2 Available Paths}
\end{figure}

\end{center}
\vspace{0.1cm}
In a case as shown above in Figure 7, if capacity permits, we will choose the path with $e_2 = 1/8$ as it the semi-boundary vertex involved is covering 7 other boundary vertices except the one in the selected augmented path. Also we will have to make changes to the edge weights like converting 1/4 to zero and the corresponding edges of the same semi boundary vertex involved to 1/3 and the semi-boundary to corresponding centre as 3. If later 1/8 weight wedge is not a part of the max flow then we simply revert back to the original weights.\\
But we realised that this problem of covering maximum number of boundary vertices is a problem reducible to the max-coverage problem, which is NP-hard. Hence the problem we are trying to solve is indeed NP-hard. The comparison is made by taking the nodes inside the partition as the subsets. (Figure 8)
\begin{center}
\begin{figure}[H]
\includegraphics[scale=0.55]{diag5.jpg}
\caption{Max-Coverage Problem}
\end{figure}
\end{center}
If there is a way where we can get minimum subsets to cover all of the universe then it is the same solution as we were trying to form which is not possible. However, we still feel that this idea of shifting centres to semi-boundary vertices could lead to some result. 
\end{itemize}
\subsection{Independent Trial}
In our attempt we start by applying the 2-approximation $K$-centre algorithm on the given graph. We then try to apply what we had learnt by reading the OPT + 1 local search algorithm of the min-degree spanning tree from section 2.6 of Williamson \& Shmoys. Effectively,if possible we transfer the load from the highest capacity nodes to lower ones through a contiguous sequence of edge assignment swaps until we reach a vertex with lower capacity as visible in the figure. \\
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{d3.jpg}
  \caption{Reassignment Through Propagation}
  \label{Figure 13}
\end{center}
\end{figure}
\textbf{Algorithm:}
\begin{algorithmic}[1]
\STATE Start with $K'$ centres of $G^2$ with no regard to capacity $L$ using the 2-approximation algorithm for uncapacitated $K$-centre.
\STATE $C \leftarrow$ set of all $K$-centres
\STATE $C^l \leftarrow$ subset of $C$ such that$\forall C \in C^l$, $C$ covers exactly $l$ clients.
\STATE In each phase:\\
\STATE \hspace{1cm}$l \leftarrow$ the maximum degree of any centre\\
\STATE \hspace{1cm}$C_l \leftarrow$ set of all centres with degree $l$
\STATE Subphase
\WHILE {there are centre with degree $l$} 
\STATE Choose a client v assigned to some centre in $C_l$.
\STATE Choose any other centre $C_m$, preferably, of maximum residual capacity, and find a path as described in Figure 9 to $C_m$. Choose the path to $C_m$ having centre-client pairs such that we can do a series of edge swaps as described in Figure 9.
\ENDWHILE
\end{algorithmic}
This is done in order to reduce the maximum number of assignments to a particular centre so as to reach the capacity $L$. This propagation is possible only when a non centre is connected to two or more centres and hence reassignment can be done.\\
But we still might have too few centres in dense areas while just sufficient in other parts or maybe even having residual capacities in sparse areas. We also have a counterexample for the same as shown in Figure 10. The centres are represented by the rectangular marks on the vertices. The leftmost centre is covering many clients within a distance of $\leq 2$ whereas the situation is the other extreme i.e. too few clients for the other centres. Thus wasting their capacity.\\
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{d1.jpg}
  \caption{Counterexample}
  \label{Figure 12}
\end{center}
\end{figure} Maybe moving to higher powers of $G$ may contribute to requiring less centres at regions where at present the centres are suffice.

Hence, from $G^2$ we move to $G^4$. Here, each centre with its clients forming a star graph will transform into a clique. The same is shown in Figure 11 below.\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.45]{d2.jpg}
  \caption{Clique formation}
  \label{Figure 10}
\end{center}
\end{figure} With such a change we might be able to merge few cliques by placing a centre on a common node of two cliques(while removing their respective centres) such that both the cliques add up to give vertices less than L.

Following this we have free centres available which we can place in dense cliques with high degree of vertices. Like in Figure 12, centres in $G^2$ are represented by square labels in the left figure and diamond label on the right while the one that replaces them in $G^4$ is represented by a square in the right figure.
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.3]{d4.jpg}
  \caption{Merging}
  \label{Figure 11}
\end{center}
\end{figure}
Why are we doing this? By doing the above $merging$ operation, we obtain an extra centre that can be placed at any location of our choice. The problem still remains on how to keep obtaining such centres other than by merging and then placing them at an appropriate position. We stop here.

Further, we tried to come up with some kind of data structure that might help us make some claims on the lower bound on K, when the edge reassignment operation stops at a local optima. \begin{figure}[H]
\includegraphics[scale=0.4]{diag8.jpg}
\caption{Level Structure}
\end{figure}
As shown above in Figure 13, we make a level structure with the set domains with centre $C_i$ by placing the domains of size $l$ at level $l$. This is the final structure after all reassignments which follows the upcoming theorems. Also edges $A,\: B \:, and \: C$ cannot be present.\\ We say it is the final structure because, after a reassignment operation, the set of neighbours of (more than or equal to 2) centres change, and also, their capacities change, thus moving them to different levels throughout the edge reassignment phase. \\\\\textbf{Theorem:}
When there can be no more edge reassignments, then no centre at level $l$ is within a distance $\leq 4$ to any node in level $l’ \geq l+2$ for all $l$. 
\\\\
\textbf{Proof:}This case is depicted in the level structure figure by edge $A$ in the level structure. After there can be no more reassignments, let there exists such a centre $C$ at a level $l$ which has an edge to some node P belonging to some level $l’ \geq l + 2$ i.e. let edge A exist. Let $C’$ be the centre covering the node $P$. Then we can do a reassignment step such that $P$ gets assigned to $C$ instead of $C`$ thereby moving $C`$ one level down and $C$ one level up. Thus the max degree can decrease this way removing one clique at a time.

This contradicts our assumption that no more reassignment is possible.\\\\
\textbf{Theorem:} When there can be no more reassignments, if a centre $C_l$ at level $l$ is within distance $\leq$ 4 to a non-centre at level $l+1$, then any centre $C'< l$ at levels $< l$, will not be within a distance $\leq$4 from any node in the domain of $C_l$.\\\\
\textbf{Proof:}
This situation is represented by edge $B$ in the level structure. We will prove by contradiction. Let us say such a case exists, i.e., edge $B$ in the figure exists. Then, we can do a series of reassignments, to reduce the degree of a centre at $C_l$ at some level $\geq l + 1$. This is a contradiction, since we assumed in the beginning that we have reached at least a local optima and there can be no more reassignments.
\section{Bibliography}
\begin{enumerate}
\item Samir Khuller, and Yoram J. Sussmann, \textit{'The Capacitated K-Center Problem'}.

\item Hyung-Chan An, Aditya Bhaskara, and Ola Svensson, \textit{'Centrality of Trees for Capacitated k-Center'}

\item David P. Williamson, and David B. Shmoys, 
\textit{The Design of Approximation Algorithms}

\item Vijay V. Vazirani, \textit{Approximation Algorithms}

\item Aounon Kumar, \textit{Network Location Problem Notes} (Work in Progress)
\end{enumerate}
\begin{appendices}
\section{The Integer Program}
\begin{center}

\begin{figure}[H]
 \includegraphics[scale=1.4]{1.png}

  \label{Figure 2}
\end{figure}

\begin{figure}[H]
 \includegraphics[scale=1.4]{2_1.png}

  \label{Figure 3}
\end{figure}

\end{center}
\section{Local Search Program}
\begin{flushleft}
\begin{figure}[H]
 \includegraphics[scale=1.4]{a.png}

  \label{Figure 4}
\end{figure}

\begin{figure}[H]
 \includegraphics[scale=1.4]{b.png}

  \label{Figure 5}
\end{figure}

\begin{figure}[H]
 \includegraphics[width=17cm,height=25cm]{c.png}

  \label{Figure 6}
\end{figure}
\begin{figure}[H]
 \includegraphics[width=17cm,height=25cm]{d.png}

\end{figure}
\begin{figure}[H]
 \includegraphics[width=10cm,height=5cm]{e.png}

\end{figure}
For the randomized local search we modify the getVmax function in the above code as:

\begin{figure}[H]
 \includegraphics[width=17cm,height=17cm]{f.png}

\end{figure}
\end{flushleft}
\section{Random Graph Generation}
This is the code snippet from the program it was used in:
\begin{figure}[H]
 \includegraphics[scale=1.2]{prajwal.png}

  \label{Figure 7}
\end{figure}
\section{Star Graph Generation}
\begin{figure}[H]
 \includegraphics[scale=1.3]{g1.png}

  \label{Figure 8}
\end{figure}

\begin{figure}[H]
\includegraphics[width=17cm,height=25cm]{g2.png}

  \label{Figure 9}
\end{figure}
\section{Unit Square Graph Generation}
\begin{figure}[H]
 \includegraphics[width=17cm,height=23cm]{us.png}

  \label{Figure 8}
\end{figure}

\end{appendices}

\end{document}
